---
title: "ECEMF model comparison plots"
output:
  html_document:
    theme: paper
    toc: true
    toc_float: 
      collapsed: false
    toc_depth: 1
params:
    charts: NULL
    regionDisplayed: "EU27"
    type: NULL
---

<!-- author: "Renato Rodrigues" -->

<style>
  .main-container {
    max-width: 95% !important;
  }
  .toc-content {
    padding-left: 0px !important;
  }
  .svg-container {
    margin: auto !important;
  }
  /* MODAL */
  /* The Modal (background) */
  .modal {
    position: fixed; /* Stay in place */
    z-index: 400; /* Sit on top */
    left: 0;
    top: 0;
    width: 100%; /* Full width */
    height: 100%; /* Full height */
    overflow: auto; /* Enable scroll if needed */
    background-color: rgb(0,0,0); /* Fallback color */
    background-color: rgba(0,0,0,0.4); /* Black w/ opacity */
  }
  
  /* Modal Content/Box */
  .modal-content {
    position: fixed;
    left: 50%;
    top: 50%;
    background-color: #fefefe;
    border: 1px solid #888;
    margin: auto;
    max-width: 96vw;
    max-height: 96vh;
    transform: translate(-50%,-50%);
  }
  
  /* The Close Button */
  .close {
    position: fixed;
    right: 0;
    color: #aaa;
    font-size: 28px;
    font-weight: bold;
    margin-right: 10px;
  }
  
  .close:hover,
  .close:focus {
    color: black;
    text-decoration: none;
    cursor: pointer;
  }

  .modal-img {
    max-width: 96vw;
      max-height: 96vh;
  }
  
  .hide {
    display:none;
  }
  
  .block{
    display:block;
  }

</style>


Description:
Model comparison for ECEMF - Summary plots.

```{r, echo=FALSE}

charts <- params$charts
regionDisplayed <- params$regionDisplayed
type <- params$type

```

<!-- Options -->
```{r Options, echo=FALSE, include=FALSE}

#chunk size and aspect ratio
chunk <- list(
  nrow1 = list(
    width = 16,
    height = 8
  ),
  nrow2 = list(
    width = 16,
    height = 8
  ),
  nrow3 = list(
    width = 16,
    height = 11.5
  )
)

#knitr::opts_chunk$set(echo = TRUE)
# setting global R chunk options (https://yihui.name/knitr/options/#chunk_options)
  knitr::opts_chunk$set(dev='svglite', # svg, png,...
                        fig.ext = ".svg",
                        #fig.asp = .8 # default aspect ratio
                        fig.width = 16,
                        fig.height = 9,
                        dpi=100
                        )

```

Regions represented in the plots:

```{r, echo=FALSE}

  if(regionDisplayed=="EU27"){
    regionsText <- paste0('
* EU27: "REMIND", "WITCH", "OSeMBE" (calculated), "Euro-Calliope" and "PRIMES"
* EU27 & UK: "MEESA"
* Europe: "IMAGE", "PROMETHEUS"   
* Europe (excl. Turkey): "TIAM-ECN"
* Europe (incl. Turkey): "MESSAGEix-GLOBIOM"`\n\n
')
  } else if(regionDisplayed=="EU28"){
    regionsText <- paste0('
* EU27 & UK: "REMIND", "WITCH", "MEESA", "OSeMBE" (calculated), "Euro-Calliope" and "PRIMES"
* Europe: "IMAGE", "PROMETHEUS"   
* Europe (excl. Turkey): "TIAM-ECN"
* Europe (incl. Turkey): "MESSAGEix-GLOBIOM"`\n\n
')
  }

```

`r paste(knitr::knit(text = regionsText))`

<!-- Display Plots -->

```{r, echo = FALSE, results='asis', fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}
if(type=="techConstraint"){
  
  out = "# Summary {.tabset}\n\n";
  out = paste0(out,"## LimBio\n\n");
  out = paste0(out,"### Biomass Primary Energy Share\n\n");
  
  cat(out)
  
  print(charts$`limBio - Biomass Primary Energy Share`)
  
  out = "\n\n";
  out = paste0(out,"### Biomass Primary Energy\n\n");
  
  cat(out)
  
  print(charts$`limBio - Biomass Primary Energy`)
  
  out = "\n\n";
  out = paste0(out,"### Biomass Secondary Energy\n\n");
  
  cat(out)
  
  print(charts$`limBio - Biomass Secondary Energy`)
  
  out = "\n\n";
  out = paste0(out,"### Biomass Electricity and Heat PE Share\n\n");
  
  cat(out)
  
  print(charts$`limBio - est. Biomass Electricity and Heat PE Share`)
  
  out = "\n\n";
  out = paste0(out,"## limCCS\n\n");
  out = paste0(out,"### Carbon Storage\n\n");
  
  cat(out)
  
  print(charts$`limCCS - Carbon Storage`)
  
  out = "\n\n";
  out = paste0(out,"### Carbon Storage per source\n\n");
  
  cat(out)
  
  print(charts$`limCCS - Carbon Storage per source`)
  
  out = "\n\n";
  out = paste0(out,"## limNuclear\n\n");
  out = paste0(out,"### Nuclear Electricity Share\n\n");
  
  cat(out)
  
  print(charts$`limNuclear - Nuclear Electricity Share`)
  
  out = "\n\n";
  out = paste0(out,"### Nuclear Primary Energy\n\n");
  
  cat(out)
  
  print(charts$`limNuclear - Nuclear Primary Energy`)
  
  out = "\n\n";
  out = paste0(out,"### Nuclear Electricity\n\n");
  
  cat(out)
  
  print(charts$`limNuclear - Nuclear Electricity`)
   
}
```




```{r summary, echo = FALSE, results='asis', fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}
if(type=="paradigmShift"){
  
  out = "# Summary {.tabset}\n\n";
  out = paste0(out,"## HighVRE\n\n");
  out = paste0(out,"### VRE Electricity Share\n\n");
  
  cat(out)
  
  print(charts$`HighVRE - VRE Electricity Share`)
  
  out = "\n\n";
  out = paste0(out,"### Total VRE Electricity\n\n");
 
  cat(out)
  
  
  print(charts$`HighVRE - Total VRE Electricity`)
  
  
  out = "\n\n";
  out = paste0(out,"### VRE Electricity per tech\n\n");
 
  cat(out)
  
  
  print(charts$`HighVRE - VRE Electricity per tech`)
  
  
  out = "\n\n";
  out = paste0(out,"## HighElectrification\n\n");
  
  out = paste0(out,"### Electricity Share in Final Energy per model\n\n");
  
  cat(out)
  
  print(charts$`HighElec - Electricity Share in Final Energy per model`)
  
  
  out = "\n\n";
  out = paste0(out,"### Electricity Share in Final Energy per scenario\n\n");
  
  cat(out)
  
  print(charts$`HighElec - Electricity Share in Final Energy per scenario`)
  
  
  out = "\n\n";
  out = paste0(out,"### Electricity Share in Industry Final Energy per scenario\n\n");
  
  cat(out)
  
  print(charts$`HighElec - Electricity Share in Industry Final Energy per scenario`)
  
  
  out = "\n\n";
  out = paste0(out,"### Electricity Share in Residential and Commercial Final Energy per scenario\n\n");
  
  cat(out)
  
  print(charts$`HighElec - Electricity Share in Residential and Commercial Final Energy per scenario`)
  
  out = "\n\n";
  out = paste0(out,"### Electricity Share in Transportation Final Energy per scenario\n\n");
  
  cat(out)
  
  print(charts$`HighElec - Electricity Share in Transportation Final Energy per scenario`)
  
  
  out = "\n\n";
  out = paste0(out,"### Total Electricity\n\n");
  
  cat(out)

  print(charts$`HighElec - Total Electricity`)
  
  
  out = "\n\n";
  out = paste0(out,"### Electricity Final Energy per sector\n\n");
  
  cat(out)
  
  print(charts$`HighElec - Electricity Final Energy per sector`)
  
  
  out = "\n\n";
  out = paste0(out,"## HighH2\n\n");
  out = paste0(out,"### Hydrogen Share in Final Energy per model\n\n");
  
  cat(out)
  
  print(charts$`HighH2 - Hydrogen Share in Final Energy per model`)
  
  
  out = "\n\n";
  out = paste0(out,"### Hydrogen Share in Final Energy per scenario\n\n");
  
  cat(out)
  
  print(charts$`HighH2 - Hydrogen Share in Final Energy per scenario`)
  
  
  out = "\n\n";
  out = paste0(out,"### Hydrogen Share in Industry Final Energy per scenario\n\n");
  
  cat(out)
  
  print(charts$`HighH2 - Hydrogen Share in Industry Final Energy per scenario`)
  
  
  out = "\n\n";
  out = paste0(out,"### Hydrogen Share in Residential and Commercial Final Energy per scenario\n\n");
  
  cat(out)
  
  print(charts$`HighH2 - Hydrogen Share in Residential and Commercial Final Energy per scenario`)
  
  out = "\n\n";
  out = paste0(out,"### Hydrogen Share in Transportation Final Energy per scenario\n\n");
  
  cat(out)
  
  print(charts$`HighH2 - Hydrogen Share in Transportation Final Energy per scenario`)
  
  
  out = "\n\n";
  out = paste0(out,"### Total Hydrogen\n\n");
  
  cat(out)
  
  print(charts$`HighH2 - Total Hydrogen`)
  
  out = "\n\n";
  out = paste0(out,"### Hydrogen Final Energy per sector\n\n");
  
  cat(out)
  
  print(charts$`HighH2 - Hydrogen Final Energy per sector`)
  
  out = "\n\n";
  out = paste0(out,"## Residual Fossil\n\n");
  out = paste0(out,"### Fossil Primary Energy Share\n\n");
  
  cat(out)
  
  print(charts$`Residual Fossil - Fossil Primary Energy Share`)
  
  out = "\n\n";
  out = paste0(out,"### Fossil Primary Energy\n\n");
  
  cat(out)
  
  print(charts$`Residual Fossil - Fossil Primary Energy`)
  
  out = "\n\n";
  out = paste0(out,"### Fossil Primary Energy per source\n\n");
 
  cat(out)
  
  print(charts$`Residual Fossil - Fossil Primary Energy per source`)
  
  out = "\n\n";
  out = paste0(out,"## High Efficiency\n\n");
  out = paste0(out,"### Final Energy\n\n");
  
  cat(out)
  
  print(charts$`HighEff - Final Energy`)
  
  
  out = "\n\n";
  out = paste0(out,"### Final Energy per sector\n\n");
 
  cat(out)
  
  print(charts$`HighEff - Final Energy per sector`)

}
```


---

# Emissions {.tabset}

## CO2

### CO2 Emissions

```{r Emissions, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`CO2 Emissions`

```

---

## per source

### CO2 Emissions per source

```{r, echo = FALSE, fig.width=chunk$nrow3$width, fig.height=chunk$nrow3$height}

charts$`CO2 emissions per source`


```


<!-- --- -->

<!-- ## NPI hist per source -->

<!-- ### NPI Historical Emissions per source -->


```{r, echo = FALSE, results='asis', fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}
if(type=="NPIhist"){
  
  out = "---\n\n";
  out = paste0(out,"## NPI hist per source\n\n");
  out = paste0(out,"### NPI Historical Emissions per source\n\n");
  
  cat(out)
  
  print(charts$`NPI Historical CO2 emissions per source`)
}
```

---

## energy and indProcesses

### Energy and Industrial Processes CO2 Emissions

```{r, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`Energy and Industrial Processes CO2 Emissions`

```

---

## energy and indProcesses detailed

### Energy and Industrial Processes CO2 Emissions detailed

```{r, echo = FALSE, fig.width=chunk$nrow3$width, fig.height=chunk$nrow3$height}

charts$`Energy and Industrial Processes CO2 Emissions detailed`

```

---

## Kyoto Gases

### Kyoto Gases Emissions

```{r, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`Kyoto Gases Emissions`

```

---

## per source

### Kyoto Gases emissions per source

```{r, echo = FALSE, fig.width=chunk$nrow3$width, fig.height=chunk$nrow3$height}

charts$`Kyoto Gases emissions per source`

```


---

## per gases

### Kyoto Gases emissions per gases

```{r, echo = FALSE, fig.width=chunk$nrow3$width, fig.height=chunk$nrow3$height}

charts$`Kyoto Gases emissions per gases`

```

---

## energy and indProcesses

### Energy and Industrial Processes Kyoto Gases

```{r, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`Energy and Industrial Processes Kyoto Gases`

```

---

## CH4

### CH4 emissions

```{r, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`CH4 Emissions`

```

---

## N2O

### N2O emissions

```{r, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`N2O Emissions`

```

---

## F-Gases

### F-Gases emissions

```{r, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`F-Gases Emissions`

```

---

# Carbon Price {.tabset}

## Carbon Price per scenario

### per scenario

```{r CarbonPrice, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`Carbon Price (per scenario)`

```

---

## Carbon Price per model

### per model

```{r, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`Carbon Price (per model)`

```

---


# Carbon Capture {.tabset}

## Carbon Capture

### Carbon Capture

```{r, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`Carbon Capture`

```

---

## per source

### Carbon Capture per source

```{r, echo = FALSE, fig.width=chunk$nrow3$width, fig.height=chunk$nrow3$height}

charts$`Carbon Capture per source`

```


---

## Carbon Storage and Usage

### Carbon Storage and Usage

```{r, echo = FALSE, fig.width=chunk$nrow3$width, fig.height=chunk$nrow3$height}

charts$`Carbon Storage and Usage`

```

---

## Carbon Removal

### Carbon Removal

```{r, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`Carbon Removal`

```

---

## per type

### Carbon Removal per type

```{r, echo = FALSE, fig.width=chunk$nrow3$width, fig.height=chunk$nrow3$height}

charts$`Carbon Removal per type`

```

---

# Primary Energy {.tabset}

## Primary Energy

### Primary Energy

```{r PrimaryEnergy, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`Primary Energy`

```

---

## per source

### Primary Energy per source

```{r, echo = FALSE, fig.width=chunk$nrow3$width, fig.height=chunk$nrow3$height}

charts$`Primary Energy per source`

```

<!-- --- -->

<!-- ## NPI hist per source -->

<!-- ### NPI Historical Primary Energy per source -->

```{r, echo = FALSE, results='asis', fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}
if(type=="NPIhist"){
  
  out = "---\n\n";
  out = paste0(out,"## NPI hist per source\n\n");
  out = paste0(out,"### NPI Historical Primary Energy per source\n\n");
  
  cat(out)
  
  print(charts$`NPI Historical Primary Energy per source`)
}
```


---

## Trade

### Primary Energy Trade

```{r, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`Primary Energy Trade`

```

---

# Primary Energy Prices {.tabset}

## Primary Energy Prices

### Primary Energy Prices per source

```{r, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`Primary Energy Price per source`

```

---

## per model

### Primary Energy Prices per model

```{r, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`Primary Energy Price per model`

```

---


# Secondary Energy {.tabset}

## Secondary Energy

### Secondary Energy

```{r SecondaryEnergy, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`Secondary Energy`

```

---

## per carrier

### Secondary Energy per carrier

```{r, echo = FALSE, fig.width=chunk$nrow3$width, fig.height=chunk$nrow3$height}

charts$`Secondary Energy per carrier`

```

<!-- --- -->


<!-- ## NPI hist per carrier -->

<!-- ### NPI Historical Secondary Energy per carrier -->


```{r, echo = FALSE, results='asis', fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}
if(type=="NPIhist"){
  
  out = "---\n\n";
  out = paste0(out,"## NPI hist per carrier\n\n");
  out = paste0(out,"### NPI Historical Secondary Energy per carrier\n\n");
  
  cat(out)
  
  print(charts$`NPI Historical Secondary Energy per carrier`)
}
```


---

## Trade

### Secondary Energy Trade

```{r, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`Trade Secondary Energy`

```

---

## Electricity

### Secondary Energy Electricity

```{r, echo = FALSE, fig.width=chunk$nrow3$width, fig.height=chunk$nrow3$height}

charts$`Secondary Energy Electricity`

```


<!-- --- -->

<!-- ## NPI hist Electricity -->

<!-- ### NPI Historical Secondary Energy Electricity -->


```{r, echo = FALSE, results='asis', fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}
if(type=="NPIhist"){
  
  out = "---\n\n";
  out = paste0(out,"## NPI hist Electricity\n\n");
  out = paste0(out,"### NPI Historical Secondary Energy Electricity\n\n");
  
  cat(out)
  
  print(charts$`NPI Historical Secondary Energy Electricity`)
}
```



---

# Secondary Energy Prices {.tabset}

## Secondary Energy Prices

### Secondary Energy Prices per carrier

```{r, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`Secondary Energy Price per carrier`

```

---

## per model

### Secondary Energy Prices per model

```{r, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`Secondary Energy Price per model`

```

---

# Final Energy {.tabset}

## Final Energy

### Final Energy

```{r FinalEnergy, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`Final Energy`

```

---

## per carrier

### Final Energy per carrier

```{r, echo = FALSE, fig.width=chunk$nrow3$width, fig.height=chunk$nrow3$height}

charts$`Final Energy per carrier`

```


<!-- --- -->

<!-- ## NPI hist per carrier -->

<!-- ### NPI Historical Final Energy per carrier -->


```{r, echo = FALSE, results='asis', fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}
if(type=="NPIhist"){
  
  out = "---\n\n";
  out = paste0(out,"## NPI hist per carrier\n\n");
  out = paste0(out,"### NPI Historical Final Energy per carrier\n\n");
  
  cat(out)
  
  print(charts$`NPI Historical Final Energy per carrier`)
}
```


---

## per sector

### Final Energy per sector

```{r, echo = FALSE, fig.width=chunk$nrow3$width, fig.height=chunk$nrow3$height}

charts$`Final Energy per sector`

```


<!-- --- -->

<!-- ## NPI hist per sector -->

<!-- ### NPI Historical Final Energy per sector -->


```{r, echo = FALSE, results='asis', fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}
if(type=="NPIhist"){
  
  out = "---\n\n";
  out = paste0(out,"## NPI hist per sector\n\n");
  out = paste0(out,"### NPI Historical Final Energy per sector\n\n");
  
  cat(out)
  
  print(charts$`NPI Historical Final Energy per sector`)
}
```



---

## Non-Energy and Industry

### Non-Energy and Industry Final Energy per carrier

```{r, echo = FALSE, fig.width=chunk$nrow3$width, fig.height=chunk$nrow3$height}

charts$`Non-Energy and Industry Final Energy per carrier`

```

---

## Buildings

### Residential and Commercial Final Energy per carrier

```{r, echo = FALSE, fig.width=chunk$nrow3$width, fig.height=chunk$nrow3$height}

charts$`Residential and Commercial Final Energy per carrier`

```

---

## Transport

### Transportation and Bunkers Final Energy per carrier

```{r, echo = FALSE, fig.width=chunk$nrow3$width, fig.height=chunk$nrow3$height}

charts$`Transportation and Bunkers Final Energy per carrier`

```

<!-- --- -->

<!-- ## Other Sectors -->

<!-- ### Other Sectors Final Energy per carrier -->

<!-- ```{r, echo = FALSE, fig.width=16, fig.height=8} -->

<!-- charts$`Other Sectors Final Energy per carrier` -->

<!-- ``` -->


---

## Transport per type

### Transportation Final Energy per type

```{r, echo = FALSE, fig.width=chunk$nrow3$width, fig.height=chunk$nrow3$height}

charts$`Transportation Final Energy per type`

```

---

## Solids, liquids and gases per source

### Final Energy solids, liquids and gases per source

```{r, echo = FALSE, fig.width=chunk$nrow3$width, fig.height=chunk$nrow3$height}

charts$`Final Energy solids, liquids and gases per source`

```

---

## Liquids per source

### Final Energy Liquids per source

```{r, echo = FALSE, fig.width=chunk$nrow3$width, fig.height=chunk$nrow3$height}

charts$`Final Energy liquids per source`

```

---

## Gases per source

### Final Energy Gases per source

```{r, echo = FALSE, fig.width=chunk$nrow3$width, fig.height=chunk$nrow3$height}

charts$`Final Energy gases per source`

```

---

## Solids per source

### Final Energy Solids per source

```{r, echo = FALSE, fig.width=chunk$nrow3$width, fig.height=chunk$nrow3$height}

charts$`Final Energy solids per source`

```



---

# Final Energy Prices {.tabset}

## Industry

### Industry Final Energy Prices per carrier

```{r, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`Industry Final Energy Price per carrier`

```

---

## per model

### Industry Final Energy Prices per model

```{r, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`Industry Final Energy Price per model`

```

---

## Residential and Commercial

### Residential and Commercial Final Energy Prices per carrier

```{r, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`Residential and Commercial Final Energy Price per carrier`

```

---

## per model

### Residential and Commercial Final Energy Prices per model

```{r, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`Residential and Commercial Final Energy Price per model`

```

---

## Transportation

### Transportation Final Energy Prices per carrier

```{r, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`Transportation Final Energy Price per carrier`

```


---

## per model

### Transportation Final Energy Prices per model

```{r, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`Transportation Final Energy Price per model`

```


---

# Economy {.tabset}

## Population

### Population

```{r Economy, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`Population`

```

---

## GDP MER

### GDP MER

```{r, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`GDP MER`

```

---

## GDP PPP

### GDP PPP

```{r, echo = FALSE, fig.width=chunk$nrow2$width, fig.height=chunk$nrow2$height}

charts$`GDP PPP`

```

---



<!-- modal code -->
<script type="text/javascript">

$(document).ready(function () {

$("img").attr("title", "click to see in fullscreen")
  
$("body").append(
'<!-- The Modal -->\
<div id="myModal" class="modal hide">\
  <!-- Modal content -->\
  <div class="modal-content">\
    <span class="close">&times;</span>\
    <div class="modal-card">\
      <img class="modal-img"\
        alt="">\
    </div>\
  </div>\
</div>').ready(function(){

  $("img").click(function(){
    src = $(this).attr("src");
    $(".modal-img").attr("src", src);
    $(".modal").removeClass("hide").addClass("block");              
  });

  $(".modal .close").click(function () {
      console.log(this);
    $(".modal").removeClass("block").addClass("hide");
  });

  $(window).click(function (event) {
    if (event.target == myModal) {
      $(".modal").removeClass("block").addClass("hide");
    }
  });

  });
});

</script>



