---
title: "ECEMP plots"
output:
  html_document:
    theme: darkly
    toc: true
    toc_float: 
      collapsed: false
    toc_depth: 1
params:
    includePattern: false    
---

<!-- author: "Renato Rodrigues" -->

<!-- the html takes ages to be created if includes pattern plots -->
<!-- therefore pattern plots are disabled by default, see includePattern: false above, -->
<!-- and should only be enabled (includePattern: true) when you want to create a final html version -->
<!-- saved png and svg files are not affected by this option and will always be created in the output folder -->


<style>
  body {
    background-color: #000000;
  }
  .main-container {
    max-width: 95% !important;
  }
  .toc-content {
    padding-left: 0px !important;
  }
  .svg-container {
    margin: auto !important;
  }
  /* MODAL */
  /* The Modal (background) */
  .modal {
    position: fixed; /* Stay in place */
    z-index: 400; /* Sit on top */
    left: 0;
    top: 0;
    width: 100%; /* Full width */
    height: 100%; /* Full height */
    overflow: auto; /* Enable scroll if needed */
    background-color: rgb(0,0,0); /* Fallback color */
    background-color: rgba(0,0,0,0.4); /* Black w/ opacity */
  }
  
  /* Modal Content/Box */
  .modal-content {
    position: fixed;
    left: 50%;
    top: 50%;
    background-color: #fefefe;
    border: 1px solid #888;
    margin: auto;
    max-width: 96vw;
    max-height: 96vh;
    transform: translate(-50%,-50%);
  }
  
  /* The Close Button */
  .close {
    position: fixed;
    right: 0;
    color: #aaa;
    font-size: 28px;
    font-weight: bold;
    margin-right: 10px;
  }
  
  .close:hover,
  .close:focus {
    color: black;
    text-decoration: none;
    cursor: pointer;
  }

  .modal-img {
    max-width: 96vw;
      max-height: 96vh;
  }
  
  .hide {
    display:none;
  }
  
  .block{
    display:block;
  }

</style>


Description:
ECEMP presentation plots.



```{r loading_libraries, echo=FALSE, include=FALSE}

#load required libraries
library(reticulate)
library(jsonlite)
library(ggplot2)
library(dplyr)
library(tidyr)
library(gridExtra)
library(grid)
library(svglite)
library(gtable)
library(ggplotify)
library(ggpattern)
library(quitte)
library("ggdark")

```


```{r chunk_options, echo=FALSE, include=FALSE}

#knitr::opts_chunk$set(echo = TRUE)
# setting global R chunk options (https://yihui.name/knitr/options/#chunk_options)
  knitr::opts_chunk$set(dev='svglite', # svg, png,...
                        fig.ext = ".svg",
                        #fig.asp = .8 # default aspect ratio
                        fig.width = 16,
                        fig.height = 9,
                        dpi=100
                        )

```


```{r loading_data, echo=FALSE, include=FALSE}

source("./R/loadData.R")

dataFile <- mostRecentData()
rdsDataPath <- paste0("./data/data_", dataFile$dateString, ".rds")

print("loading previously calculated data")
df <- readRDS(rdsDataPath)

#reducing number of decimal places
df$Value <- round(df$Value,3)

#Selecting region
region <- "EU28"

if(region=="EU27"){
  df <- df[((df$Region %in% c("EU27", "Europe", "Europe (excl. Turkey)", "Europe (incl. Turkey)") & !(df$Model == "Euro-Calliope") ) | (df$Model == "MEESA" & df$Region == "EU27 & UK") | (df$Model == "Euro-Calliope" & df$Region == "EU27")),]
} else if (region=="EU28"){
  df <- df[(df$Region %in% c("EU27 & UK", "Europe", "Europe (excl. Turkey)", "Europe (incl. Turkey)") & !(df$Model == "Euro-Calliope") ) | (df$Model == "Euro-Calliope" & df$Region == "Europe"),] 
} else {
  df <- df[(df$Region %in% region),] 
}

# create output folder if it does not exist
dir.create("./output", showWarnings = FALSE) # create the output main folder
dir.create(paste0("./output/", dataFile$dateString), showWarnings = FALSE) 
outputFolder <- paste0("./output/", dataFile$dateString, "/ECEMP_charts")
dir.create(outputFolder, showWarnings = FALSE) # create the output folder

```


```{r aesthetics, echo=FALSE, include=FALSE}

source("./R/aesthetics.R") # load aesthetics

# overwrite colors for black theme
color["Solids"] = "#616161"

#plot aesthetics
baseSize <- 24

theme_dark <- function(){
  dark_theme_gray(base_size = baseSize) +
    theme(
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      axis.text.x = element_text(angle=90, hjust = 1, vjust = 0.5),
      #legend.position="bottom",
      legend.title=element_blank(),
      legend.key.size = unit(20/16*baseSize,"pt"),
      legend.text = element_text(size=10/16*baseSize), #, margin = margin(r = 20, unit = 'pt')
      panel.spacing = unit(1.5, "lines"),
      strip.background=element_rect(fill="black"),
      panel.background = element_rect(fill="#1f1f1f"),
      panel.grid.minor = element_line(size = 0.5, linetype="dotted"),
      panel.grid.major = element_line(size = 1)
    )
}

```

<!-- Plots -->

```{r, echo=FALSE, include=FALSE}

g <- NULL

```

# CO2 Emissions {.tabset}

## C400-lin

```{r creating_co2_emissions_plot, echo=FALSE, include=FALSE}

vars <- list(
  "Emissions|CO2"
)

scenario <- c("DIAG-C400-lin")

year <- sort(unique(df$Period)[unique(df$Period) >= 2005 & unique(df$Period) <= 2050])

plotData <- df[df$Period %in% year & df$Scenario %in% scenario & df$Variable %in% unlist(vars),]

# Order
plotData$Model <- factor(plotData$Model , levels = c("Euro-Calliope","IMAGE","MEESA","MESSAGE","OSeMBE","PRIMES","PROMETHEUS","REMIND","TIAM-ECN","WITCH"))

g[["CO2 Emissions"]] <- ggplot(plotData,aes(x=Period,y=Value,color=Model)) +
    geom_hline(yintercept=0, color = "black", size=2, alpha = 1) +
    geom_vline(xintercept=2020, color = "black", size=1.5, alpha = 1) +
    geom_line(size=1) +
    geom_point() +
    theme_dark() +
    #facet_wrap(~Scenario) +
    scale_color_manual(values = setNames(color[levels(plotData$Model)],levels(plotData$Model))) #+
    #ylab("CO2 Emissions (Mt CO2/yr)")

ggsave(paste0(outputFolder,"/CO2_Emissions_C400.svg"), g[["CO2 Emissions"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
ggsave(paste0(outputFolder,"/CO2_Emissions_C400.png"), g[["CO2 Emissions"]] , device="png", width = 12, height = 8, dpi=100, units = "in")
```

```{r co2_emissions, echo=FALSE, fig.width=12, fig.height=8}

  g[["CO2 Emissions"]]

```

## C400 and NPI

```{r creating_co2_emissions_per_sector_plot, echo=FALSE, include=FALSE}

vars <- list(
  "Emissions|CO2"
)

scenario <- c("DIAG-NPI", "DIAG-C400-lin")

year <- sort(unique(df$Period)[unique(df$Period) >= 2005 & unique(df$Period) <= 2050])

plotData <- df[df$Period %in% year & df$Scenario %in% scenario & df$Variable %in% unlist(vars),]

# Order
plotData$Model <- factor(plotData$Model , levels = c("Euro-Calliope","IMAGE","MEESA","MESSAGE","OSeMBE","PRIMES","PROMETHEUS","REMIND","TIAM-ECN","WITCH"))

g[["CO2 Emissions per scenario"]] <- ggplot(plotData,aes(x=Period,y=Value,color=Model,linetype=Scenario)) +
    geom_hline(yintercept=0, color = "black", size=2, alpha = 1) +
    geom_vline(xintercept=2020, color = "black", size=1.5, alpha = 1) +
    geom_line(size=1) +
    geom_point() +
    theme_dark() +
    scale_color_manual(values = setNames(color[levels(plotData$Model)],levels(plotData$Model))) +
    scale_linetype_manual(values = c("DIAG-NPI"="dashed", "DIAG-C400-lin"="solid")) +
    guides(color  = guide_legend(order = 2),
         linetype = guide_legend(order = 1)) #+
    #ylab("CO2 Emissions (Mt CO2/yr)")

ggsave(paste0(outputFolder,"/CO2_Emissions_per_scenario.svg"), g[["CO2 Emissions per scenario"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
ggsave(paste0(outputFolder,"/CO2_Emissions_per_scenario.png"), g[["CO2 Emissions per scenario"]] , device="png", width = 12, height = 8, dpi=100, units = "in")
```


```{r co2_emissions_per_sector, echo=FALSE, fig.width=12, fig.height=8}

  g[["CO2 Emissions per scenario"]]

```



# Primary Energy Biomass {.tabset}

## C400-lin

```{r creating_pe_biomass_plot, echo=FALSE, include=FALSE}

vars <- list(
  "Primary Energy|Biomass"
)

scenario <- c("DIAG-C400-lin")

year <- sort(unique(df$Period)[unique(df$Period) >= 2005 & unique(df$Period) <= 2050])

plotData <- df[df$Period %in% year & df$Scenario %in% scenario & df$Variable %in% unlist(vars),]

# Order
plotData$Model <- factor(plotData$Model , levels = c("Euro-Calliope","IMAGE","MEESA","MESSAGE","OSeMBE","PRIMES","PROMETHEUS","REMIND","TIAM-ECN","WITCH"))

g[["PE Biomass"]] <- ggplot(plotData,aes(x=Period,y=Value,color=Model)) +
    geom_hline(yintercept=0, color = "black", size=2, alpha = 1) +
    geom_vline(xintercept=2020, color = "black", size=1.5, alpha = 1) +
    geom_line(size=1) +
    geom_point() +
    theme_dark() +
    #facet_wrap(~Scenario) +
    scale_color_manual(values = setNames(color[levels(plotData$Model)],levels(plotData$Model))) #+
    #ylab("Primary Energy Biomass (EJ/yr)")

ggsave(paste0(outputFolder,"/PE_Biomass_C400.svg"), g[["PE Biomass"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
ggsave(paste0(outputFolder,"/PE_Biomass_C400.png"), g[["PE Biomass"]] , device="png", width = 12, height = 8, dpi=100, units = "in")
```

```{r pe_biomass, echo=FALSE, fig.width=12, fig.height=8}

  g[["PE Biomass"]]

```


# Final Energy per sector {.tabset}

## C400-lin

```{r creating_final_energy_per_sector_plot, echo=FALSE, include=FALSE}

vars <- list(
  "Non-Energy Use"=c(
    "Hydrogen"="Final Energy|Non-Energy Use|Hydrogen",
    "Gases"   ="Final Energy|Non-Energy Use|Gases",
    "Liquids" ="Final Energy|Non-Energy Use|Liquids",
    "Solids"  ="Final Energy|Non-Energy Use|Solids",
    "Other"   ="Final Energy|Non-Energy Use|Other"
  ),
  "Industry"=c(
    "Hydrogen"="Final Energy|Industry|Hydrogen",
    "Gases"   ="Final Energy|Industry|Gases",
    "Liquids" ="Final Energy|Industry|Liquids",
    "Solids"  ="Final Energy|Industry|Solids",
    "Other"   ="Final Energy|Industry|Other",
    "Heat"    ="Final Energy|Industry|Heat",
    "Electricity"="Final Energy|Industry|Electricity"
  ),
  "Buildings"=c(
    "Hydrogen"="Final Energy|Residential and Commercial|Hydrogen",
    "Gases"   ="Final Energy|Residential and Commercial|Gases",
    "Liquids" ="Final Energy|Residential and Commercial|Liquids",
    "Solids"  ="Final Energy|Residential and Commercial|Solids",
    "Other"   ="Final Energy|Residential and Commercial|Other",
    "Heat"    ="Final Energy|Residential and Commercial|Heat",
    "Electricity"="Final Energy|Residential and Commercial|Electricity"
  ),
  "Bunkers"=c(
    "Hydrogen"="Final Energy|Bunkers|Hydrogen",
    "Gases"   ="Final Energy|Bunkers|Gases",
    "Liquids" ="Final Energy|Bunkers|Liquids",
    "Other"   ="Final Energy|Bunkers|Other",
    "Electricity"="Final Energy|Bunkers|Electricity"
  ),
  "Transport"=c(
    "Hydrogen"="Final Energy|Transportation|Hydrogen",
    "Gases"   ="Final Energy|Transportation|Gases",
    "Liquids" ="Final Energy|Transportation|Liquids",
    "Other"   ="Final Energy|Transportation|Other",
    "Electricity"="Final Energy|Transportation|Electricity"
  )
)

groups <- c(
  "Non-Energy Use"="Industry",
  "Industry"="Industry",
  "Buildings"="Buildings",
  "Bunkers"="Transport",
  "Transport"="Transport"
)

pattern <- c(
  "Non-Energy Use"="stripe",
  "Industry"="none",
  "Buildings"="none",
  "Bunkers"="stripe",
  "Transport"="none"
)

scenario <- c("DIAG-C400-lin")

year <- c(2050)

plotData <- df[df$Period %in% year & df$Scenario %in% scenario & df$Variable %in% unlist(vars),]

varTosector <- NULL
carriers <- NULL
for(sector in names(vars)){
  tmp <- unlist(vars[[sector]])
  tmp2 <- rep(sector,length(tmp))
  names(tmp2) <- tmp
  varTosector <- c(varTosector, tmp2)
  carrier_tmp <- setNames(names(unlist(vars[[sector]])),unlist(vars[[sector]]))
  carriers <- c(carriers, carrier_tmp)
}

plotData$Sector <- varTosector[plotData$Variable]

plotData$Group <- groups[plotData$Sector]

plotData$Carrier <- carriers[plotData$Variable] 

# Order
plotData$Model <- factor(plotData$Model , levels = c("Euro-Calliope","IMAGE","MEESA","MESSAGE","OSeMBE","PRIMES","PROMETHEUS","REMIND","TIAM-ECN","WITCH"))
plotData$Carrier <- factor(plotData$Carrier , levels = c("Hydrogen","Gases","Liquids","Solids","Other","Heat","Electricity"))
plotData$Sector <- factor(plotData$Sector , levels = c("Industry","Non-Energy Use","Buildings","Transport","Bunkers"))
plotData$Group <- factor(plotData$Group , levels = c("Industry","Buildings","Transport"))

g[["final_energy_per_sector_with_pattern"]] <- ggplot(plotData,aes(x=Model,y=Value,fill=Carrier,pattern=Sector)) +
  geom_hline(yintercept=0, color = "black", size=2, alpha = 1) +
  geom_bar_pattern(stat='identity', pattern_key_scale_factor = 0.3, pattern_density=0.3, pattern_spacing = 0.03, pattern_colour = "white", pattern_fill = "white", pattern_alpha=0.4) +
  theme_dark() +
  facet_wrap(~Group) +
  scale_fill_manual(values = setNames(color[levels(plotData$Carrier)],levels(plotData$Carrier))) +
  scale_pattern_manual(values = pattern, breaks=c("Non-Energy Use","Bunkers")) +
  guides(fill  = guide_legend(order = 1, override.aes = list(pattern = "none")),
         pattern = guide_legend(order = 2, override.aes = list(fill = NA))) #+
  #ylab("Final Energy per sector (EJ/yr)")

g[["final_energy_per_sector"]] <- ggplot(plotData,aes(x=Model,y=Value,fill=Carrier,pattern=Sector)) +
  geom_hline(yintercept=0, color = "black", size=2, alpha = 1) +
  geom_bar(stat='identity') +
  theme_dark() +
  facet_wrap(~Group) +
  scale_fill_manual(values = setNames(color[levels(plotData$Carrier)],levels(plotData$Carrier))) #+
  #ylab("Final Energy per sector (EJ/yr)") 

ggsave(paste0(outputFolder,"/FE_perSector_C400_2050.svg"), g[["final_energy_per_sector_with_pattern"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
ggsave(paste0(outputFolder,"/FE_perSector_C400_2050.png"), g[["final_energy_per_sector_with_pattern"]] , device="png", width = 12, height = 8, dpi=100, units = "in")

```

```{r Final_energy_per_sector, echo=FALSE, fig.width=12, fig.height=8}

  if(params$includePattern){
    g[["final_energy_per_sector_with_pattern"]]
  } else {
    g[["final_energy_per_sector"]]
  }

```

---




# Final Energy Electricity shares {.tabset}


```{r creating_final_energy_elec_share_plots, echo=FALSE, include=FALSE}

vars <- list(
  "Total"=c(
    "Final Energy|Electricity Share"
  ),
  "Industry"=c(
    "Final Energy|Industry|Electricity Share"
  ),
  "Buildings"=c(
    "Final Energy|Residential and Commercial|Electricity Share"
  ),
  "Transport"=c(
    "Final Energy|Transportation|Electricity Share"
  )
)

scenario <- c("DIAG-C400-lin")

year <- sort(unique(df$Period)[unique(df$Period) >= 2005 & unique(df$Period) <= 2050])

plotData <- df[df$Period %in% year & df$Scenario %in% scenario & df$Variable %in% unlist(vars),]

varTosector <- setNames(names(unlist(vars)),unlist(vars))
plotData$Sector <- varTosector[plotData$Variable]

# Order
plotData$Model <- factor(plotData$Model , levels = c("Euro-Calliope","IMAGE","MEESA","MESSAGE","OSeMBE","PRIMES","PROMETHEUS","REMIND","TIAM-ECN","WITCH"))
plotData$Sector <- factor(plotData$Sector , levels = c("Total","Industry","Buildings","Transport"))

g[["final_energy_elec_share"]] <- ggplot(plotData,aes(x=Period,y=Value,color=Model)) +
    geom_hline(yintercept=0, color = "black", size=2, alpha = 1) +
    geom_vline(xintercept=2020, color = "black", size=1.5, alpha = 1) +
    geom_line(size=1) +
    geom_point() +
    theme_dark() +
    facet_wrap(~Sector) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0, 1, by = 0.2), limits = c(0,1)) +
    scale_color_manual(values = setNames(color[levels(plotData$Model)],levels(plotData$Model))) #+
    #ylab("Final Energy Electricity shares (%)")


ggsave(paste0(outputFolder,"/FE_electShare_C400.svg"), g[["final_energy_elec_share"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
ggsave(paste0(outputFolder,"/FE_electShare_C400.png"), g[["final_energy_elec_share"]] , device="png", width = 12, height = 8, dpi=100, units = "in")


### total Electricity share

vars <- list(
  "Final Energy|Electricity Share"
)

scenario <- c("DIAG-C400-lin")

year <- sort(unique(df$Period)[unique(df$Period) >= 2005 & unique(df$Period) <= 2050])

plotData <- df[df$Period %in% year & df$Scenario %in% scenario & df$Variable %in% unlist(vars),]

# Order
plotData$Model <- factor(plotData$Model , levels = c("Euro-Calliope","IMAGE","MEESA","MESSAGE","OSeMBE","PRIMES","PROMETHEUS","REMIND","TIAM-ECN","WITCH"))

g[["final_energy_elec_share_total"]] <- ggplot(plotData,aes(x=Period,y=Value,color=Model)) +
    geom_hline(yintercept=0, color = "black", size=2, alpha = 1) +
    geom_vline(xintercept=2020, color = "black", size=1.5, alpha = 1) +
    geom_line(size=1) +
    geom_point() +
    theme_dark() +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0, 1, by = 0.2), limits = c(0,1)) +
    scale_color_manual(values = setNames(color[levels(plotData$Model)],levels(plotData$Model))) #+
    #ylab("Final Energy Electricity shares (%)")

ggsave(paste0(outputFolder,"/FE_electShare_total_C400.svg"), g[["final_energy_elec_share_total"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
ggsave(paste0(outputFolder,"/FE_electShare_total_C400.png"), g[["final_energy_elec_share_total"]] , device="png", width = 12, height = 8, dpi=100, units = "in")


### Electricity share per sector

vars <- list(
  "Industry"=c(
    "Final Energy|Industry|Electricity Share"
  ),
  "Buildings"=c(
    "Final Energy|Residential and Commercial|Electricity Share"
  ),
  "Transport"=c(
    "Final Energy|Transportation|Electricity Share"
  )
)

scenario <- c("DIAG-C400-lin")

year <- sort(unique(df$Period)[unique(df$Period) >= 2005 & unique(df$Period) <= 2050])

plotData <- df[df$Period %in% year & df$Scenario %in% scenario & df$Variable %in% unlist(vars),]

varTosector <- setNames(names(unlist(vars)),unlist(vars))
plotData$Sector <- varTosector[plotData$Variable]

# Order
plotData$Model <- factor(plotData$Model , levels = c("Euro-Calliope","IMAGE","MEESA","MESSAGE","OSeMBE","PRIMES","PROMETHEUS","REMIND","TIAM-ECN","WITCH"))
plotData$Sector <- factor(plotData$Sector , levels = c("Industry","Buildings","Transport"))

g[["final_energy_elec_share_sector"]] <- ggplot(plotData,aes(x=Period,y=Value,color=Model)) +
    geom_hline(yintercept=0, color = "black", size=2, alpha = 1) +
    geom_vline(xintercept=2020, color = "black", size=1.5, alpha = 1) +
    geom_line(size=1) +
    geom_point() +
    theme_dark() +
    facet_wrap(~Sector) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0, 1, by = 0.2), limits = c(0,1)) +
    scale_color_manual(values = setNames(color[levels(plotData$Model)],levels(plotData$Model))) +
    #ylab("Final Energy Electricity shares (%)") +
    theme(legend.position="bottom")

ggsave(paste0(outputFolder,"/FE_electShare_per_sector_C400.svg"), g[["final_energy_elec_share_sector"]] , device="svg", width = 12, height = 6, dpi=100, units = "in")
ggsave(paste0(outputFolder,"/FE_electShare_per_sector_C400.png"), g[["final_energy_elec_share_sector"]] , device="png", width = 12, height = 6, dpi=100, units = "in")


# merge plot

g[["final_energy_elec_share_panel"]] <- grid.arrange(
  g[["final_energy_elec_share_total"]] + theme(plot.margin=margin(10,70,10,70)) + ylab(NULL) + theme(plot.title = element_text(hjust = 0.5)), # + ggtitle("Final Energy Electricity shares (%)")
  g[["final_energy_elec_share_sector"]] + theme(legend.position = "none") + ylab(NULL),
  #widths = c(8, 6, 2),
  layout_matrix = rbind(c(1, 1, 1, 1),
                        c(1, 1, 1, 1),
                        c(2, 2, 2, 2),
                        c(2, 2, 2, 2))
)

ggsave(paste0(outputFolder,"/FE_electShare_panel_C400.svg"), g[["final_energy_elec_share_panel"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
ggsave(paste0(outputFolder,"/FE_electShare_panel_C400.png"), g[["final_energy_elec_share_panel"]] , device="png", width = 12, height = 8, dpi=100, units = "in")


```

## Panel

```{r, echo=FALSE, fig.width=12, fig.height=8}

  plot(g[["final_energy_elec_share_panel"]])

```

## Total

```{r, echo=FALSE, fig.width=12, fig.height=8}

  g[["final_energy_elec_share_total"]]

```

## Sector

```{r, echo=FALSE, fig.width=12, fig.height=6}

  g[["final_energy_elec_share_sector"]]

```

## Facets

```{r, echo=FALSE, fig.width=12, fig.height=8}

  g[["final_energy_elec_share"]]

```

```{r creating_final_energy_elec_share_box_plots, echo=FALSE, include=FALSE}

### total Electricity share Box Plot

vars <- list(
  "Final Energy|Electricity Share"
)

scenario <- c("DIAG-NPI","DIAG-C400-lin")

year <- sort(unique(df$Period)[unique(df$Period) >= 2005 & unique(df$Period) <= 2050])

plotData <- df[df$Period %in% year & df$Scenario %in% scenario & df$Variable %in% unlist(vars),]

# Order
plotData$Model <- factor(plotData$Model , levels = c("Euro-Calliope","IMAGE","MEESA","MESSAGE","OSeMBE","PRIMES","PROMETHEUS","REMIND","TIAM-ECN","WITCH"))

g[["final_energy_elec_share_total_box_plot"]] <- ggplot(plotData,aes(x=Period, y=Value, fill=Scenario, group=interaction(Period,Scenario))) +
    geom_boxplot() + 
    theme_dark() +
  scale_fill_manual(values = c("DIAG-NPI"="#395B64","DIAG-C400-lin"="570A57")) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0, 1, by = 0.2), limits = c(0,1)) +
    # ylab("Final Energy Electricity shares (%)") +
    theme(legend.position="bottom")

ggsave(paste0(outputFolder,"/FE_electShare_total_per_scenario_box_plot.svg"), g[["final_energy_elec_share_total_box_plot"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
ggsave(paste0(outputFolder,"/FE_electShare_total_per_scenario_box_plot.png"), g[["final_energy_elec_share_total_box_plot"]] , device="png", width = 12, height = 8, dpi=100, units = "in")

```

## Total box plot

```{r, echo=FALSE, fig.width=12, fig.height=8}

  g[["final_energy_elec_share_total_box_plot"]]

```



```{r creating_final_energy_elec_share_per_sector_box_plots, echo=FALSE, include=FALSE}

### total Electricity share per sector Box Plot

vars <- list(
  "Industry"=c(
    "Final Energy|Industry|Electricity Share"
  ),
  "Buildings"=c(
    "Final Energy|Residential and Commercial|Electricity Share"
  ),
  "Transport"=c(
    "Final Energy|Transportation|Electricity Share"
  )
)

scenario <- c("DIAG-NPI","DIAG-C400-lin")

year <- sort(unique(df$Period)[unique(df$Period) >= 2005 & unique(df$Period) <= 2050])

plotData <- df[df$Period %in% year & df$Scenario %in% scenario & df$Variable %in% unlist(vars),]

varTosector <- setNames(names(unlist(vars)),unlist(vars))
plotData$Sector <- varTosector[plotData$Variable]

# Order
plotData$Model <- factor(plotData$Model , levels = c("Euro-Calliope","IMAGE","MEESA","MESSAGE","OSeMBE","PRIMES","PROMETHEUS","REMIND","TIAM-ECN","WITCH"))
plotData$Sector <- factor(plotData$Sector , levels = c("Industry","Buildings","Transport"))

g[["final_energy_elec_share_per_sector_box_plot"]] <- ggplot(plotData,aes(x=Period, y=Value, fill=Scenario, group=interaction(Period,Scenario))) +
    geom_boxplot() + 
    theme_dark() +
    facet_wrap(~Sector) +
    scale_fill_manual(values = c("DIAG-NPI"="#395B64","DIAG-C400-lin"="570A57")) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0, 1, by = 0.2), limits = c(0,1)) +
    #ylab("Final Energy Electricity shares (%)") +
    theme(legend.position="bottom")

ggsave(paste0(outputFolder,"/FE_electShare_per_sector_per_scenario_box_plot.svg"), g[["final_energy_elec_share_per_sector_box_plot"]] , device="svg", width = 12, height = 6, dpi=100, units = "in")
ggsave(paste0(outputFolder,"/FE_electShare_per_sector_per_scenario_box_plot.png"), g[["final_energy_elec_share_per_sector_box_plot"]] , device="png", width = 12, height = 6, dpi=100, units = "in")

```

## Per sector box plot

```{r, echo=FALSE, fig.width=12, fig.height=6}

  g[["final_energy_elec_share_per_sector_box_plot"]]

```


# Final Energy Hydrogen shares {.tabset}


```{r creating_final_energy_h2_share_plots, echo=FALSE, include=FALSE}

vars <- list(
  "Total"=c(
    "Final Energy|Hydrogen Share"
  ),
  "Industry"=c(
    "Final Energy|Industry|Hydrogen Share"
  ),
  "Buildings"=c(
    "Final Energy|Residential and Commercial|Hydrogen Share"
  ),
  "Transport"=c(
    "Final Energy|Transportation|Hydrogen Share"
  )
)

scenario <- c("DIAG-C400-lin")

year <- sort(unique(df$Period)[unique(df$Period) >= 2005 & unique(df$Period) <= 2050])

plotData <- df[df$Period %in% year & df$Scenario %in% scenario & df$Variable %in% unlist(vars),]

varTosector <- setNames(names(unlist(vars)),unlist(vars))
plotData$Sector <- varTosector[plotData$Variable]

# Order
plotData$Model <- factor(plotData$Model , levels = c("Euro-Calliope","IMAGE","MEESA","MESSAGE","OSeMBE","PRIMES","PROMETHEUS","REMIND","TIAM-ECN","WITCH"))
plotData$Sector <- factor(plotData$Sector , levels = c("Total","Industry","Buildings","Transport"))

g[["final_energy_h2_share"]] <- ggplot(plotData,aes(x=Period,y=Value,color=Model)) +
    geom_hline(yintercept=0, color = "black", size=2, alpha = 1) +
    geom_vline(xintercept=2020, color = "black", size=1.5, alpha = 1) +
    geom_line(size=1) +
    geom_point() +
    theme_dark() +
    facet_wrap(~Sector) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0, 1, by = 0.2), limits = c(0,1)) +
    scale_color_manual(values = setNames(color[levels(plotData$Model)],levels(plotData$Model))) #+
    #ylab("Final Energy Hydrogen shares (%)")


ggsave(paste0(outputFolder,"/FE_h2Share_C400.svg"), g[["final_energy_h2_share"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
ggsave(paste0(outputFolder,"/FE_h2Share_C400.png"), g[["final_energy_h2_share"]] , device="png", width = 12, height = 8, dpi=100, units = "in")


### total Hydrogen share

vars <- list(
  "Final Energy|Hydrogen Share"
)

scenario <- c("DIAG-C400-lin")

year <- sort(unique(df$Period)[unique(df$Period) >= 2005 & unique(df$Period) <= 2050])

plotData <- df[df$Period %in% year & df$Scenario %in% scenario & df$Variable %in% unlist(vars),]

# Order
plotData$Model <- factor(plotData$Model , levels = c("Euro-Calliope","IMAGE","MEESA","MESSAGE","OSeMBE","PRIMES","PROMETHEUS","REMIND","TIAM-ECN","WITCH"))

g[["final_energy_h2_share_total"]] <- ggplot(plotData,aes(x=Period,y=Value,color=Model)) +
    geom_hline(yintercept=0, color = "black", size=2, alpha = 1) +
    geom_vline(xintercept=2020, color = "black", size=1.5, alpha = 1) +
    geom_line(size=1) +
    geom_point() +
    theme_dark() +
    #facet_wrap(~Scenario) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0, 1, by = 0.2), limits = c(0,1)) +
    scale_color_manual(values = setNames(color[levels(plotData$Model)],levels(plotData$Model))) #+
    #ylab("Final Energy Hydrogen shares (%)")

ggsave(paste0(outputFolder,"/FE_h2Share_total_C400.svg"), g[["final_energy_h2_share_total"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
ggsave(paste0(outputFolder,"/FE_h2Share_total_C400.png"), g[["final_energy_h2_share_total"]] , device="png", width = 12, height = 8, dpi=100, units = "in")


### Hydrogen share per sector

vars <- list(
  "Industry"=c(
    "Final Energy|Industry|Hydrogen Share"
  ),
  "Buildings"=c(
    "Final Energy|Residential and Commercial|Hydrogen Share"
  ),
  "Transport"=c(
    "Final Energy|Transportation|Hydrogen Share"
  )
)

scenario <- c("DIAG-C400-lin")

year <- sort(unique(df$Period)[unique(df$Period) >= 2005 & unique(df$Period) <= 2050])

plotData <- df[df$Period %in% year & df$Scenario %in% scenario & df$Variable %in% unlist(vars),]

varTosector <- setNames(names(unlist(vars)),unlist(vars))
plotData$Sector <- varTosector[plotData$Variable]

# Order
plotData$Model <- factor(plotData$Model , levels = c("Euro-Calliope","IMAGE","MEESA","MESSAGE","OSeMBE","PRIMES","PROMETHEUS","REMIND","TIAM-ECN","WITCH"))
plotData$Sector <- factor(plotData$Sector , levels = c("Industry","Buildings","Transport"))

g[["final_energy_h2_share_sector"]] <- ggplot(plotData,aes(x=Period,y=Value,color=Model)) +
    geom_hline(yintercept=0, color = "black", size=2, alpha = 1) +
    geom_vline(xintercept=2020, color = "black", size=1.5, alpha = 1) +
    geom_line(size=1) +
    geom_point() +
    theme_dark() +
    facet_wrap(~Sector) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0, 1, by = 0.2), limits = c(0,1)) +
    scale_color_manual(values = setNames(color[levels(plotData$Model)],levels(plotData$Model))) +
    #ylab("Final Energy Hydrogen shares (%)") +
    theme(legend.position="bottom")


ggsave(paste0(outputFolder,"/FE_h2Share_per_sector_C400.svg"), g[["final_energy_h2_share_sector"]] , device="svg", width = 12, height = 6, dpi=100, units = "in")
ggsave(paste0(outputFolder,"/FE_h2Share_per_sector_C400.png"), g[["final_energy_h2_share_sector"]] , device="png", width = 12, height = 6, dpi=100, units = "in")


# merge plot

g[["final_energy_h2_share_panel"]] <- grid.arrange(
  g[["final_energy_h2_share_total"]] + theme(plot.margin=margin(10,70,10,70)) + ylab(NULL) + theme(plot.title = element_text(hjust = 0.5)), #+ ggtitle("Final Energy Hydrogen shares (%)") 
  g[["final_energy_h2_share_sector"]] + theme(legend.position = "none") + ylab(NULL),
  #widths = c(8, 6, 2),
  layout_matrix = rbind(c(1, 1, 1, 1),
                        c(1, 1, 1, 1),
                        c(2, 2, 2, 2),
                        c(2, 2, 2, 2))
)

ggsave(paste0(outputFolder,"/FE_h2Share_panel_C400.svg"), g[["final_energy_h2_share_panel"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
ggsave(paste0(outputFolder,"/FE_h2Share_panel_C400.png"), g[["final_energy_h2_share_panel"]] , device="png", width = 12, height = 8, dpi=100, units = "in")


```

## Panel

```{r, echo=FALSE, fig.width=12, fig.height=8}

  plot(g[["final_energy_h2_share_panel"]])

```

## Total

```{r, echo=FALSE, fig.width=12, fig.height=8}

  g[["final_energy_h2_share_total"]]

```

## Sector

```{r, echo=FALSE, fig.width=12, fig.height=6}

  g[["final_energy_h2_share_sector"]]

```

## Facets

```{r, echo=FALSE, fig.width=12, fig.height=8}

  g[["final_energy_h2_share"]]

```


```{r creating_final_energy_h2_share_box_plots, echo=FALSE, include=FALSE}

### total Hydrogen share Box Plot

vars <- list(
  "Final Energy|Hydrogen Share"
)

scenario <- c("DIAG-NPI","DIAG-C400-lin")

year <- sort(unique(df$Period)[unique(df$Period) >= 2005 & unique(df$Period) <= 2050])

plotData <- df[df$Period %in% year & df$Scenario %in% scenario & df$Variable %in% unlist(vars),]

# Order
plotData$Model <- factor(plotData$Model , levels = c("Euro-Calliope","IMAGE","MEESA","MESSAGE","OSeMBE","PRIMES","PROMETHEUS","REMIND","TIAM-ECN","WITCH"))

g[["final_energy_h2_share_total_box_plot"]] <- ggplot(plotData,aes(x=Period, y=Value, fill=Scenario, group=interaction(Period,Scenario))) +
    geom_boxplot() + 
    theme_dark() +
    scale_fill_manual(values = c("DIAG-NPI"="#395B64","DIAG-C400-lin"="570A57")) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0, 1, by = 0.2), limits = c(0,1)) +
    #ylab("Final Energy Hydrogen shares (%)") +
    theme(legend.position="bottom")

ggsave(paste0(outputFolder,"/FE_h2Share_total_per_scenario_box_plot.svg"), g[["final_energy_h2_share_total_box_plot"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
ggsave(paste0(outputFolder,"/FE_h2Share_total_per_scenario_box_plot.png"), g[["final_energy_h2_share_total_box_plot"]] , device="png", width = 12, height = 8, dpi=100, units = "in")

```

## Total box plot

```{r, echo=FALSE, fig.width=12, fig.height=8}

  g[["final_energy_h2_share_total_box_plot"]]

```



```{r creating_final_energy_h2_share_per_sector_box_plots, echo=FALSE, include=FALSE}

### total Hydrogen share per sector Box Plot

vars <- list(
  "Industry"=c(
    "Final Energy|Industry|Hydrogen Share"
  ),
  "Buildings"=c(
    "Final Energy|Residential and Commercial|Hydrogen Share"
  ),
  "Transport"=c(
    "Final Energy|Transportation|Hydrogen Share"
  )
)

scenario <- c("DIAG-NPI","DIAG-C400-lin")

year <- sort(unique(df$Period)[unique(df$Period) >= 2005 & unique(df$Period) <= 2050])

plotData <- df[df$Period %in% year & df$Scenario %in% scenario & df$Variable %in% unlist(vars),]

varTosector <- setNames(names(unlist(vars)),unlist(vars))
plotData$Sector <- varTosector[plotData$Variable]

# Order
plotData$Model <- factor(plotData$Model , levels = c("Euro-Calliope","IMAGE","MEESA","MESSAGE","OSeMBE","PRIMES","PROMETHEUS","REMIND","TIAM-ECN","WITCH"))
plotData$Sector <- factor(plotData$Sector , levels = c("Industry","Buildings","Transport"))

g[["final_energy_h2_share_per_sector_box_plot"]] <- ggplot(plotData,aes(x=Period, y=Value, fill=Scenario, group=interaction(Period,Scenario))) +
    geom_boxplot() + 
    theme_dark() +
    facet_wrap(~Sector) +
    scale_fill_manual(values = c("DIAG-NPI"="#395B64","DIAG-C400-lin"="570A57")) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0, 1, by = 0.2), limits = c(0,1)) +
    #ylab("Final Energy Hydrogen shares (%)") +
    theme(legend.position="bottom")

ggsave(paste0(outputFolder,"/FE_h2Share_per_sector_per_scenario_box_plot.svg"), g[["final_energy_h2_share_per_sector_box_plot"]] , device="svg", width = 12, height = 6, dpi=100, units = "in")
ggsave(paste0(outputFolder,"/FE_h2Share_per_Sector_per_scenario_box_plot.png"), g[["final_energy_h2_share_per_sector_box_plot"]] , device="png", width = 12, height = 6, dpi=100, units = "in")

```

## Per sector box plot

```{r, echo=FALSE, fig.width=12, fig.height=6}

  g[["final_energy_h2_share_per_sector_box_plot"]]

```


# Kyoto gases {.tabset}

## C400-lin

```{r creating_emissions_per_gases_plot, echo=FALSE, include=FALSE}

vars <- list(
  "F-Gases"="Emissions|F-Gases",
  "N2O"="Emissions|Kyoto Gases|N2O",
  "CH4"="Emissions|Kyoto Gases|CH4",
  "CO2"="Emissions|CO2"
)

scenario <- c("DIAG-C400-lin")

year <- c(2050)

plotData <- df[df$Period %in% year & df$Scenario %in% scenario & df$Variable %in% unlist(vars),]

# Order
plotData$Model <- factor(plotData$Model , levels = c("Euro-Calliope","IMAGE","MEESA","MESSAGE","OSeMBE","PRIMES","PROMETHEUS","REMIND","TIAM-ECN","WITCH"))
plotData$Variable <- factor(plotData$Variable , levels = unlist(vars))

total <- plotData %>%
      group_by(Model,Scenario,Region,Period) %>%
      summarize(Value = sum(Value, na.rm = TRUE),.groups="drop")

g[["Emissions_per_gases"]] <- ggplot(plotData,aes(x=Model,y=Value,fill=Variable)) +
  geom_hline(yintercept=0, color = "black", size=2, alpha = 1) +
  geom_bar(stat='identity') +
  geom_point(data=total,aes(x=Model,y=Value), shape=23,fill="black",color="white", alpha = 0.7,show.legend = F, size = 2, stroke = 2) +
  theme_dark() +
#  facet_wrap(~Scenario+Period) +
  scale_fill_manual(values = setNames(color[names(vars)],vars), labels=setNames(names(vars),vars)) +
 # ylab("Emissions per gases (Mt CO2e/yr)") +
  scale_x_discrete(drop=FALSE)

ggsave(paste0(outputFolder,"/Emissions_per_gases_C400_2050.svg"), g[["Emissions_per_gases"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
ggsave(paste0(outputFolder,"/Emissions_per_gases_C400_2050.png"), g[["Emissions_per_gases"]] , device="png", width = 12, height = 8, dpi=100, units = "in")


```

```{r emissions_per_gases, echo=FALSE, fig.width=12, fig.height=8}

  g[["Emissions_per_gases"]]
  
```


<!-- modal code -->
<script type="text/javascript">

$(document).ready(function () {

$("img").attr("title", "click to see in fullscreen")
  
$("body").append(
'<!-- The Modal -->\
<div id="myModal" class="modal hide">\
  <!-- Modal content -->\
  <div class="modal-content">\
    <span class="close">&times;</span>\
    <div class="modal-card">\
      <img class="modal-img"\
        alt="">\
    </div>\
  </div>\
</div>').ready(function(){

  $("img").click(function(){
    src = $(this).attr("src");
    $(".modal-img").attr("src", src);
    $(".modal").removeClass("hide").addClass("block");              
  });

  $(".modal .close").click(function () {
      console.log(this);
    $(".modal").removeClass("block").addClass("hide");
  });

  $(window).click(function (event) {
    if (event.target == myModal) {
      $(".modal").removeClass("block").addClass("hide");
    }
  });

  });
});

</script>



