---
title: "WP1 NetZero scenario charts"
output:
  html_document:
    theme: paper
    toc: true
    toc_float:
      collapsed: false
    toc_depth: 3
params:
  regions: c("EU27 & UK", "EU27")
  scenario: "WP1 NetZero"
  dataFolder: "../output"
---


<style>
  .main-container {
    max-width: 95% !important;
  }
  .toc-content {
    padding-left: 0px !important;
  }
  .svg-container {
    margin: auto !important;
  }
  img {
    max-width: 100% !important;
    <!-- display: block !important; -->
    margin-left: auto !important;
    margin-right: auto !important;
  }
  .hideChart {
    display: none;
  }
</style>


Description:

ECEMF working package 1.3: `r params$scenario` scenario results.


```{r include=FALSE}
# Settings for knitting html from this notebook

library(svglite)
library(ggplot2)

# setting global R chunk options (https://yihui.name/knitr/options/#chunk_options)
  knitr::opts_chunk$set(dev='svglite', # svg, png,...
                        fig.ext = ".svg",
                        #fig.asp = .8 # default aspect ratio
                        fig.width = 12,
                        fig.height = 6,
                        dpi=100,
						dev.args = list(fix_text_size = FALSE, user_fonts = list(sans = list(plain = "../font/static/OpenSans-Regular.ttf",italic = "../font/static/OpenSans-Italic.ttf")))
                        )

```



```{r loading_data, include=FALSE}

g <- list()
for(r in params$regions){
  g[[r]] <- readRDS(paste0(params$dataFolder,"/individualCharts/charts_", r, ".rds"))
}

```



```{r, include=FALSE}

# Creating dashboard sections
processText <- function(tree){
  recursiveText <- function(subTree,title,regions,level=NULL, output=""){
    out <- ""
    #level <- c(level,paste0("[['", title , "']]"))
    level <- c(level,title)
    if(!(is.ggplot(subTree[["chart"]]))){
    #if(!(is.ggplot(subTree))){
      if(is.ggplot(subTree[[1]][["chart"]])){
      #if(is.ggplot(subTree[[1]])){
        #print(paste0("secn = ", title))
        #print(level)
        #out <- paste0(out,knitr::knit_expand(text="\n---\n\n"))
        out <- paste0(out,knitr::knit_expand(text=paste0(strrep("#", length(level)), " ", title, " {.tabset}\n\n")))
        for(varName in names(subTree)){
          print(paste0("varName=",varName))
          #cleanName <- gsub("^\\|+", "",gsub(paste0(level, collapse = "|"), "", var))
          #cleanName <- ifelse(cleanName %in% c("|",""), "Total", cleanName)
          #print(cleanName)
          #out <- paste0(out,knitr::knit_expand(text="\n---\n\n"))
          out <- paste0(out,knitr::knit_expand(text=paste0(strrep("#",length(level) + 1), " ", varName, "\n\n")))
          out <- paste0(out,"```{r , echo=FALSE}\n\n")
          for(r in regions){
            out <- paste0(out,"g[['", r, "']]", paste(paste0("[['", level, "']]"), collapse = "") ,"[['", varName, "']][['chart']]\n\n")
          }
          out <- paste0(out,"```\n\n")
          out <- paste0(out,knitr::knit_expand(text="\n---\n\n"))
        }
        #print(out)
        output <- paste0(output,out)
        #return(output)
      } else {
        print(paste0("main = ", title))
        #print(level)
        #print("next level")
        #out <- paste0(out,knitr::knit_expand(text="\n---\n\n"))
        out <- paste0(out,knitr::knit_expand(text=paste0(strrep("#",length(level)), " ", title, " \n\n")))
        output <- paste0(output,out)
        print(out)
        #print(paste0("title = ", title, ", level =", level))
        for(title2 in names(subTree)){
          #print(paste0("next = ", title2))
          #print(paste0("title2 = ", title2))
          output <- recursiveText(subTree[[title2]],title2,regions,level,output)
          #return(recursiveText(subTree[[title2]],title2,regions,level,paste0(output,out)))
        }
      }
    }
    return(output)
  }
  o <- ""
  for(t in names(tree[[1]])){
    o <- paste0(o,recursiveText(tree[[1]][[t]], t, names(tree)))
  }
  return(o)
}
   
result <- ""
result <- processText(g)

#cat(result,file="output.txt", append=FALSE)

```
  
  
`r paste(knitr::knit(text = paste(result, collapse = '\n')))`


```{r, include=FALSE}

# javascript code for region selector

  dropdownText = paste0("<div id=\'regionsSelector\' class=\'dropdown\' style=\'position: fixed; right: 10px; top: 10px;\'><button class=\'btn btn-default btn-sm dropdown-toggle\' type=\'button\' id=\'dropdownMenu1\' data-toggle=\'dropdown\' aria-haspopup=\'true\' aria-expanded=\'false\'>", names(g)[1], "<span class=\'caret\'></span></button><ul class=\'dropdown-menu dropdown-menu-right\' aria-labelledby=\'dropdownMenu1\'>")
  i = 0
  for(r in names(g)){
    dropdownText = paste0(dropdownText,"<li><a data-value=\'", i, "\'>", r, "</a></li>")
    i = i +1
  }
  dropdownText = paste0(dropdownText,"</ul></div>")
  
  jsScriptText <- ""
  jsScriptText = paste0(jsScriptText,knitr::knit_expand(text="\n\n"))
  jsScriptText = paste0(jsScriptText,knitr::knit_expand(text="<script type='text/javascript'>\n"))
  jsScriptText = paste0(jsScriptText,knitr::knit_expand(text="var currRegion = 0;\n"))
  jsScriptText = paste0(jsScriptText,knitr::knit_expand(text="var currChart = 0;\n"))
  jsScriptText = paste0(jsScriptText,knitr::knit_expand(text=paste0("var regionsNumber = ", length(names(g)), ";\n")))
  jsScriptText = paste0(jsScriptText,knitr::knit_expand(text=paste0("var regions = [", toString(dQuote(names(g))),"] ;\n")))
  jsScriptText = paste0(jsScriptText,knitr::knit_expand(text=paste0("var dropdownText =", '"',  dropdownText, '"', ";\n")))
  jsScriptText = paste0(jsScriptText,knitr::knit_expand(text="</script>"))
 
#fileConn<-file("jsScriptText.txt")
#writeLines(jsScriptText, fileConn)
#close(fileConn)  
  
# fileConn<-file("dropdownText.txt")
# writeLines(dropdownText, fileConn)
# close(fileConn)
  
```

`r paste(knitr::knit(text = paste(jsScriptText, collapse = '\n')))`

<!-- creating the region selector -->
<script type="text/javascript">
  
$(window).on( "load", function() {

  $(".tab-content > .section").each(function(){
    $charts = $(this).find("img");
    $charts.addClass("hideChart");
    totalCharts = $charts.length/regionsNumber;
    for (i = 0; i < $charts.length; i++){
        $charts.eq(i).addClass("region_" + Math.floor(i/totalCharts));
        $charts.eq(i).addClass("chartType_" + i%totalCharts);
    }
    $(this).find(".chartType_" + currChart + ".region_" + currRegion).removeClass("hideChart");
  })

  $("#header").append(dropdownText);

  $("#regionsSelector a").click(function() {
    prevRegion = currRegion;
    currRegion = $(this).data("value");
    console.log(prevRegion + " -> " + currRegion);
    $(".tab-content > .section").each(function(){
      $(this).find(".chartType_" + currChart + ".region_" + prevRegion).addClass("hideChart");
      $(this).find(".chartType_" + currChart + ".region_" + currRegion).removeClass("hideChart");
    })
    $("#dropdownMenu1").text($('#regionsSelector a[data-value="' + currRegion  + '"]').text());
    $("#dropdownMenu1").append("<span class=\'caret\'></span>");
  })

});

</script>


