---
title: "WP1 NetZero scenario charts"
output:
  html_document:
    theme: paper
    toc: true
    toc_float:
      collapsed: false
    toc_depth: 3
params:
  regions: c("EU27 & UK", "EU27")
  scenario: "WP1 NetZero"
  models: c("REMIND")
  dataFolder: "../output"
---


<style>
  .main-container {
    max-width: 95% !important;
  }
  .toc-content {
    padding-left: 0px !important;
  }
  .svg-container {
    margin: auto !important;
  }
  img {
    max-width: 100% !important;
    <!-- display: block !important; -->
    margin-left: auto !important;
    margin-right: auto !important;
  }
  .hideChart {
    display: none;
  }
</style>


Description:

ECEMF working package 1.3: `r params$scenario` scenario results.


```{r include=FALSE}
# Settings for knitting html from this notebook

library(svglite)
library(ggplot2)

# setting global R chunk options (https://yihui.name/knitr/options/#chunk_options)
  knitr::opts_chunk$set(dev='svglite', # svg, png,...
                        fig.ext = ".svg",
                        #fig.asp = .8 # default aspect ratio
                        fig.width = 12,
                        fig.height = 6,
                        dpi=100,
						dev.args = list(fix_text_size = FALSE, user_fonts = list(sans = list(plain = "../font/static/OpenSans-Regular.ttf",italic = "../font/static/OpenSans-Italic.ttf")))
                        )
print("aaaa")
```



```{r loading_data, include=FALSE}
# creating charts
#source("./historicalValues.R")

# load data
#source("./R/mostRecentData.R")
#dataFile <- mostRecentData()
#outFolder <- paste0("./output/", dataFile$dateString)

g <- list()
#models <- NULL

#params$regions <- cleanFileName(unique(data$region))
#params$models <- unique(data$model)
#params$dataFolder <- "../output/2024_03_13_16.18.05"
#getwd()

models <- sort(params$models)
for(r in params$regions){
  for (m in models){
  #for (f in list.files(paste0(params$dataFolder, "/modelChanges/"), paste0(r, "_modelChanges*"))){
    #m <- unlist(unlist(strsplit(f,"_|\\.")))[3]
    #models <- c(models, m)
    g[[r]][[m]] <- readRDS(paste0(params$dataFolder,"/modelChanges/", r, "_modelChanges_", m, ".rds"))
  }
}

#message("data loaded")
# g <- list()
# for(r in names(params$regions)){
# #for(r in c("EU27 & UK (*)", "EU27 (*)")){
#   #regionfilename <- gsub("\\(\\)| +","",gsub("[\\\\/:*?\"<>|]","",r))
#   g[[params$regions[r]]] <- readRDS(paste0(params$dataFolder,"/modelChangesCharts_", r, ".rds"))
# }
# #gg <- readRDS(paste0(params$dataFolder,"/charts.rds"))
# #g <- gg[params$regions]

#models <- names(g[[1]])

```



```{r, include=FALSE}

# Creating dashboard sections
processText <- function(tree){
  recursiveText <- function(subTree,title,regions,level=NULL, output=""){
    out <- ""
    #level <- c(level,paste0("[['", title , "']]"))
    level <- c(level,title)
    if(is.null(subTree[["chart"]])){
    #if(!(is.ggplot(subTree[["chart"]]))){
    #if(!(is.ggplot(subTree))){
      if(!(is.null(subTree[[1]][["chart"]]))){
      #if(is.ggplot(subTree[[1]][["chart"]])){
      #if(is.ggplot(subTree[[1]])){
        #print(paste0("secn = ", title))
        #print(level)
        #out <- paste0(out,knitr::knit_expand(text="\n---\n\n"))
        out <- paste0(out,knitr::knit_expand(text=paste0(strrep("#", length(level)), " ", title, " {.tabset}\n\n")))
        for(varName in names(subTree)){
          print(paste0("varName=",varName))
          #cleanName <- gsub("^\\|+", "",gsub(paste0(level, collapse = "|"), "", var))
          #cleanName <- ifelse(cleanName %in% c("|",""), "Total", cleanName)
          #print(cleanName)
          #out <- paste0(out,knitr::knit_expand(text="\n---\n\n"))
          out <- paste0(out,knitr::knit_expand(text=paste0(strrep("#",length(level) + 1), " ", varName, "\n\n")))
          #out <- paste0(out,"```{r , echo=FALSE}\n\n")
          for(r in regions){
            out <- paste0(out,"<div class='regionGroup' data-region='", r , "'>\n\n")
            for(m in models){
              out <- paste0(out,"<div class='modelGroup' data-model='", m , "'>\n\n")
              out <- paste0(out,"```{r , echo=FALSE}\n\n")
              #out <- paste0(out,"```{r , echo=FALSE, class.source='", r, ", ", m ,"'}\n\n")
              print(paste0(out,"g[['", r, "']][['", m, "']]", paste(paste0("[['", level, "']]"), collapse = "") ,"[['", varName, "']][['chart']]\n\n"))
              out <- paste0(out,"g[['", r, "']][['", m, "']]", paste(paste0("[['", level, "']]"), collapse = "") ,"[['", varName, "']][['chart']]\n\n")
              
              out <- paste0(out,"```\n\n")
              out <- paste0(out,"</div>\n\n")
            }
            out <- paste0(out,"</div>\n\n")
          }
          #out <- paste0(out,"```\n\n")
          out <- paste0(out,knitr::knit_expand(text="\n---\n\n"))
        }
        #print(out)
        output <- paste0(output,out)
        #return(output)
      } else {
        print(paste0("main = ", title))
        #print(level)
        #print("next level")
        #out <- paste0(out,knitr::knit_expand(text="\n---\n\n"))
        out <- paste0(out,knitr::knit_expand(text=paste0(strrep("#",length(level)), " ", title, " \n\n")))
        output <- paste0(output,out)
        print(out)
        #print(paste0("title = ", title, ", level =", level))
        for(title2 in names(subTree)){
          #print(paste0("next = ", title2))
          #print(paste0("title2 = ", title2))
          output <- recursiveText(subTree[[title2]],title2,regions,level,output)
          #return(recursiveText(subTree[[title2]],title2,regions,level,paste0(output,out)))
        }
      }
    }
    return(output)
  }
  o <- ""
  for(t in names(tree[[1]][[1]])){
    o <- paste0(o,recursiveText(tree[[1]][[1]][[t]], t, names(tree)))
  }
  return(o)
}
   
result <- ""
result <- processText(g)

#cat(result,file="output.txt", append=FALSE)

```
  
  
`r paste(knitr::knit(text = paste(result, collapse = '\n')))`


```{r, include=FALSE}

# javascript code for region selector

  dropDownsText = paste0("<div style=\'position: fixed; right: 10px; top: 10px;\'>")
  dropDownsText = paste0(dropDownsText,"<div id=\'regionsSelector\' class=\'dropdown\'><button class=\'btn btn-default btn-sm dropdown-toggle\' type=\'button\' id=\'dropdownMenuRegion\' data-toggle=\'dropdown\' aria-haspopup=\'true\' aria-expanded=\'false\'>", names(g)[1], "<span class=\'caret\'></span></button><ul class=\'dropdown-menu dropdown-menu-right\' aria-labelledby=\'dropdownMenuRegion\'>")
  for(r in names(g)){
    dropDownsText = paste0(dropDownsText,"<li><a data-value=\'", r, "\'>", r, "</a></li>")
  }
  dropDownsText = paste0(dropDownsText,"</ul></div>")
  
  dropDownsText = paste0(dropDownsText,"<div id=\'modelsSelector\' class=\'dropdown\'><button class=\'btn btn-default btn-sm dropdown-toggle\' type=\'button\' id=\'dropdownMenuModel\' data-toggle=\'dropdown\' aria-haspopup=\'true\' aria-expanded=\'false\'>", models[1], "<span class=\'caret\'></span></button><ul class=\'dropdown-menu dropdown-menu-right\' aria-labelledby=\'dropdownMenuModel\'>")
  for(m in models){
    dropDownsText = paste0(dropDownsText,"<li><a data-value=\'", m, "\'>", m, "</a></li>")
  }
  dropDownsText = paste0(dropDownsText,"</ul></div></div>")
  
  jsScriptText <- ""
  jsScriptText = paste0(jsScriptText,knitr::knit_expand(text="\n\n"))
  jsScriptText = paste0(jsScriptText,knitr::knit_expand(text="<script type='text/javascript'>\n"))
  # jsScriptText = paste0(jsScriptText,knitr::knit_expand(text="var currRegion = 0;\n"))
  # jsScriptText = paste0(jsScriptText,knitr::knit_expand(text="var currChart = 0;\n"))
  # jsScriptText = paste0(jsScriptText,knitr::knit_expand(text=paste0("var regionsNumber = ", length(names(g)), ";\n")))
  # jsScriptText = paste0(jsScriptText,knitr::knit_expand(text=paste0("var regions = [", toString(dQuote(names(g))),"] ;\n")))
  
  jsScriptText = paste0(jsScriptText,knitr::knit_expand(text=paste0("var currRegion = '", names(g)[1], "';\n")))
  jsScriptText = paste0(jsScriptText,knitr::knit_expand(text=paste0("var currModel = '", models[1], "';\n")))
  
  jsScriptText = paste0(jsScriptText,knitr::knit_expand(text=paste0("var dropDownsText =", '"',  dropDownsText, '"', ";\n")))
  jsScriptText = paste0(jsScriptText,knitr::knit_expand(text="</script>"))
 
#fileConn<-file("jsScriptText.txt")
#writeLines(jsScriptText, fileConn)
#close(fileConn)  
  
# fileConn<-file("regionsdropdownText.txt")
# writeLines(regionsdropdownText, fileConn)
# close(fileConn)
  
```

`r paste(knitr::knit(text = paste(jsScriptText, collapse = '\n')))`

<!-- creating the region selector -->
<script type="text/javascript">
  
$(window).on( "load", function() {

  $(".regionGroup").each(function(){
    reg = $(this).attr("data-region");
    if(reg != currRegion)
      $(this).addClass("hideChart");
  })
  
  $(".modelGroup").each(function(){
    model = $(this).attr("data-model");
    if(model != currModel)
      $(this).addClass("hideChart");
  })

  $("#header").append(dropDownsText);

  $("#regionsSelector a").click(function() {
    prevRegion = currRegion;
    currRegion = $(this).data("value");
    console.log(prevRegion + " -> " + currRegion);
    $(".regionGroup[data-region='" + prevRegion + "']").addClass("hideChart");
    $(".regionGroup[data-region='" + currRegion + "']").removeClass("hideChart");
    $("#dropdownMenuRegion").text($('#regionsSelector a[data-value="' + currRegion  + '"]').text());
    $("#dropdownMenuRegion").append("<span class=\'caret\'></span>");
  })
  
  $("#modelsSelector a").click(function() {
    prevModel = currModel;
    currModel = $(this).data("value");
    console.log(prevModel + " -> " + currModel);
    $(".modelGroup[data-model='" + prevModel + "']").addClass("hideChart");
    $(".modelGroup[data-model='" + currModel + "']").removeClass("hideChart");
    $("#dropdownMenuModel").text($('#modelsSelector a[data-value="' + currModel  + '"]').text());
    $("#dropdownMenuModel").append("<span class=\'caret\'></span>");
  })

});

</script>


