---
title: "Policy Brief plots"
output:
  html_document:
    theme: paper
    toc: true
    toc_float: 
      collapsed: false
    toc_depth: 3
params:
  df: NULL
  hist: NULL
  chartsFolder: FALSE
  save: FALSE
---


<style>
  .main-container {
    max-width: 95% !important;
  }
  .toc-content {
    padding-left: 0px !important;
  }
  .svg-container {
    margin: auto !important;
  }
  /* MODAL */
  /* The Modal (background) */
  .modal {
    position: fixed; /* Stay in place */
    z-index: 400; /* Sit on top */
    left: 0;
    top: 0;
    width: 100%; /* Full width */
    height: 100%; /* Full height */
    overflow: auto; /* Enable scroll if needed */
    background-color: rgb(0,0,0); /* Fallback color */
    background-color: rgba(0,0,0,0.4); /* Black w/ opacity */
  }
  
  /* Modal Content/Box */
  .modal-content {
    position: fixed;
    left: 50%;
    top: 50%;
    background-color: #fefefe;
    border: 1px solid #888;
    margin: auto;
    max-width: 96vw;
    max-height: 96vh;
    transform: translate(-50%,-50%);
  }
  
  /* The Close Button */
  .close {
    position: fixed;
    right: 0;
    color: #aaa;
    font-size: 28px;
    font-weight: bold;
    margin-right: 10px;
  }
  
  .close:hover,
  .close:focus {
    color: black;
    text-decoration: none;
    cursor: pointer;
  }

  .modal-img {
    max-width: 96vw;
      max-height: 96vh;
  }
  
  .hide {
    display:none;
  }
  
  .block{
    display:block;
  }

</style>


Description:
Policy Brief plots.


```{r loading_libraries, echo=FALSE, include=FALSE}

#load required libraries
library(reticulate)
library(jsonlite)
library(ggplot2)
library(dplyr)
library(tidyr)
library(gridExtra)
library(grid)
library(svglite)
library(gtable)
library(ggplotify)
library(ggpattern)
library(quitte)
library("ggdark")
library(knitr)
library(kableExtra)
library(piamInterfaces)

```


```{r chunk_options, echo=FALSE, include=FALSE}

#knitr::opts_chunk$set(echo = TRUE)
# setting global R chunk options (https://yihui.name/knitr/options/#chunk_options)
  knitr::opts_chunk$set(dev='svglite', # svg, png,...
                        fig.ext = ".svg",
                        #fig.asp = .8 # default aspect ratio
                        fig.width = 16,
                        fig.height = 9,
                        dpi=100
                        )

```

```{r loading_data, echo=FALSE, include=FALSE}

df <- params$df
hist <- params$hist %>%
  rename(source = model) %>%
  select(-scenario)
chartsFolder <- params$chartsFolder
saveCharts <- params$save


# temporarily resize TIAM Emissions|Kyoto Gases|AFOLU|Land
if(max(df %>% filter(model == "TIAM-ECN", variable == "Emissions|Kyoto Gases|AFOLU|Land") %>% pull(value)) > 10000){
  df <- df %>% 
    mutate(value = ifelse(model == "TIAM-ECN" & variable == "Emissions|Kyoto Gases|AFOLU|Land", value/1000, value))
}

```



```{r aesthetics, echo=FALSE, include=FALSE}

model.colors <- c(
    #model
    "IMAGE" = "#00ffff",
    "Euro-Calliope" = "#c0c0c0",
    "MEESA" = "#ff00ff",
    "MESSAGE" = "#800080",
    "OSeMBE" = "#a52a2a",
    "PRIMES" = "#0000ff",
    "PROMETHEUS" = "#ffd900",
    "REMIND" = "#ff6347",
    "LIMES" = "#ffaf47",
    "TIAM-ECN" = "#4682b4",
    "WITCH" = "#228b22"
  )

color <- c(
  #model
  "IMAGE" = "#00ffff",
  "Euro-Calliope" = "#c0c0c0",
  "MEESA" = "#ff00ff",
  "x MEESA" = "#ff00ff",
  "MESSAGE" = "#800080",
  "OSeMBE" = "#a52a2a",
  "x OSeMBE" = "#a52a2a",
  "PRIMES" = "#0000ff",
  "PROMETHEUS" = "#ffd900",
  "REMIND" = "#ff6347",
  "LIMES" = "#ffaf47",
  "TIAM-ECN" = "#4682b4",
  "WITCH" = "#228b22",
  #scenario
  "DIAG-Base" = "#f1746e",
  "DIAG-NPI" = "#b49f06",
  "DIAG-C80-gr5" = "#2eba38",
  "DIAG-C0to80-gr5" = "#38c0c4",
  "DIAG-C400-lin" = "#939dff",
  "DIAG-NZero" = "#f062e4",
  
  "DIAG-C400-lin-LimBio" = "#005900",
  "DIAG-C400-lin-LimCCS" = "#999959",
  "DIAG-C400-lin-LimNuclear" = "#ff33ff",
  
  "DIAG-C400-lin-HighVRE" = "#337fff",
  "DIAG-C400-lin-HighElectrification" = "#ffb200",
  "DIAG-C400-lin-HighH2" = "#5ed5b0",
  "DIAG-C400-lin-ResidualFossil" = "#cccccc",
  "DIAG-C400-lin-HighEff" = "#2eba38",
  
  #emi
  "Energy Supply" = "#3D4849",
  "Energy Supply - Elect and Heat" = "#FF6600",
  "Energy Supply - Electricity"= "#ffb200",
  "Energy Supply - Heat"= "#cc0000",
  "Energy Supply - Fuels" = "#4D4D93",
  "Energy Supply - Gases"= "#999959",
  "Energy Supply - Liquids"= "#0000cc",
  "Energy Supply - Solids"= "#0c0c0c",
  "Energy Supply - Other" = "#79a6d2",
  "Energy Supply - Hydrogen" = "#5ed5b0",
  "Energy Demand" = "#999959",
  "Energy Demand - Transportation" = "#a1dd70",
  "Energy Demand - Bunkers" = "#ffc0cb",
  "Energy Demand - Buildings" = "#5edfff",
  "Energy Demand - Residential and Commercial" = "#5edfff",
  "Energy Demand - Other Sector" = "#999959",
  "Demand - AFOFI" = "#005900",
  "Energy Demand - Industry" = "#5f6769",
  "Industrial Processes" = "#5c5c5c",
  "Other" = "#5b0d8f",
  "Waste" = "#A52A2A",
  "AFOLU" = "#4DAF4A",
  "AFOLU - Agriculture" = "#357933",
  "AFOLU - LULUCF" = "#6ec16b",
  
  "non CO2" = "#ffe7a0",
  "Other Removal (e.g. DACCS)"="#CC6666",
  "CO2 - Energy and Industrial Processes"="#5f6769",
  "CO2 - AFOLU"="#4DAF4A",
  "CO2 - Waste"="#A52A2A",
  "CO2 - Other"="#5b0d8f",
  "CO2 - Other Removal (e.g. DACCS)"="#CC6666",	
  
  "CO2 - Energy and Industrial Processes without bunkers" = "#5f6769",
  "CO2 - Bunkers" = "#ffc0cb",
  
  #capture
  "CCS" = "#cccccc",
  "CCS - Biomass" = "#008c00",
  "CCS - Biomass Energy" = "#005900",
  "CCS - Biomass Industry" = "#377EB8",
  "CCS - Biomass Industrial Processes" = "#79a6d2",
  "CCS - Fossil" = "#cccccc",
  "CCS - Fossil Energy" = "#a6a6a6",
  "CCS - Fossil Industry" = "#4e4e4e",
  "CCS - Fossil Industrial Processes" = "#282828",
  "DAC" = "#CC6666",
  "Enhanced Weathering" = "#5b0d8f",
  "Land Use" = "#4DAF4A",
  "Other" = "#79a6d2",
  #carrier
  "Electricity" = "#ffb200",
  "Heat"        = "#cc0000",
  "Hydrogen"    = "#5ed5b0",
  "Gases"       = "#999959",
  "Gases - Fossil"  = "#999959", # #a1a161",
  "Gases - Biomass" = "#00cc00", #"#005900", # "#999959",
  "Gases - Electricity"  = "#fef3da", #"#ffb200", # "#caca8a",
  "Natural gas"  = "#999959", # #a1a161",
  "Biogas" = "#00cc00", #"#005900", # "#999959",
  "Syngas"  = "#fef3da", #"#ffb200", # "#caca8a",
  "Ocean" = "#5ed5f0",
  
  "Liquids"     = "#0000cc",
  "Liquids - Fossil"  = "#0000cc", #"#000068",
  "Liquids - Biomass" = "#005900", #"#0000cc",
  "Liquids - Electricity"   = "#ffb200", #"#5050ff",
  "Solids"      = "#0c0c0c",
  "Solids - Fossil"  = "#0c0c0c",
  "Solids - Biomass" = "#0f3c08", #"#005900",
  "Other Carrier" = "#79a6d2",
  "Geothermal" = "#e51900",
  "Solar" = "#ffcc00",
  #sector
  "Non-Energy Use" = "#ff9966",
  "Industry" = "#5f6769",
  "Residential and Commercial" = "#5edfff",
  "Transportation" = "#a1dd70",
  "Bunkers" = "#ffc0cb",
  "Other Sector" = "#999959",
  #sector fe carrier
  "Non-Energy Use - Hydrogen" = "#5ed5b0",
  "Non-Energy Use - Gases" = "#999959",
  "Non-Energy Use - Liquids" = "#0000cc",
  "Non-Energy Use - Solids" = "#0c0c0c",
  "Non-Energy Use - Other" = "#79a6d2",
  "Industry - Electricity" = "#ffb200",
  "Industry - Heat" = "#cc0000",
  "Industry - Hydrogen" = "#5ed5b0",
  "Industry - Gases" = "#999959",
  "Industry - Liquids" = "#0000cc",
  "Industry - Solids" = "#0c0c0c",
  "Industry - Other" = "#79a6d2",
  "Transport - Electricity" = "#ffb200",
  "Transport - Hydrogen" = "#5ed5b0",
  "Transport - Gases" = "#999959",
  "Transport - Liquids" = "#0000cc",
  "Transport - Other" = "#79a6d2",
  "Bunkers - Electricity" = "#ffb200",
  "Bunkers - Hydrogen" = "#5ed5b0",
  "Bunkers - Gases" = "#999959",
  "Bunkers - Liquids" = "#0000cc",
  "Bunkers - Other" = "#79a6d2",
  #sector per type
  "Passenger" = "#77c3e6",
  "Freight" = "#37474f",
  #tech
  "Solar" = "#ffcc00",
  "Solar CSP" = "#ffcc00",
  "Solar PV" = "#ffe600",
  "Wind" = "#337fff",
  "Wind Offshore" = "#4d33ff",
  "Wind Onshore" = "#337fff",
  "Other" = "#5b0d8f",
  "Ocean" = "#0000FF",
  "Biomass" = "#005900",
  "Biomass w/ CCS" = "#33ff00",
  "Biomass w/o CCS" = "#005900",
  "Hydro" = "#191999",
  "Hydro Reservoir" = "#8a8aec",
  "Hydro Pumped Storage" = "#dfdffa",
  "Hydro Run of River" = "#191999",
  "Geothermal" = "#e51900",
  "Nuclear" = "#ff33ff",
  "Gas" = "#999959",
  "Gas CCGT" = "#7c6b2a",
  "Gas w/ CCS" = "#b79e38",
  "Gas w/o CCS" = "#999959",
  "Coal" = "#0c0c0c",
  "Coal w/ CCS" = "#5c5c5c",
  "Coal w/o CCS" = "#0c0c0c",
  "Oil" = "#b30000",
  "Oil w/ CCS" = "#ff6565",
  "Oil w/o CCS" = "#b30000",
  
  "VRE" = "#337fff",
  "non VRE" = "#ececec",
  
  "Hydrogen w/ CCS"="#86e0c4",
  "Hydrogen w/o CCS"="#5ed5b0",
  "Electricity w/ CCS"="#ffc133",
  "Electricity w/o CCS"="#ffb200",  
  "Liquids w/ CCS" = "#0000ff",
  "Liquids w/o CCS" = "#0000cc",
  
  #Carbon management
  "Direct Air Capture" = "#24A19C",
  "Fossil" = "#cccccc",
  "Storage" = "#D96098",
  "Usage" = "#325288",
  #Kyoto Gases
  "CO2" = "#7e7e7e",
  "CH4" = "#ffe7a0",
  "N2O" = "#44ba97",
  "F-Gases" = "#ff9977"
)

alpha = c(
  #hist
  "EU27Ref" = 0.4,
  "Eurostat" = 1,
  "IMF" = 1,           
  "2019 Eurostat" = 1
)

linetype = c(
  "INNOPATHS"="twodash",
  "James_IHME"= "dotted",
  "James_IMF"="dotdash",
  "James_WB"= "12345678",
  "EDGE_SSP1"="1F",
  "EDGE_SSP2"="twodash",
  "EU_Referencescenario_2016"= "dotted",
  "Eurostat"="dotdash",
  "IEA"= "12345678",
  "JRC"="1F",
  "BP"="twodash",
  "Ember"= "dotted",
  "UNFCCC"="solid",
  "CEDS"= "12345678",
  "EDGAR6"="1F",
  "WDI"="twodash"
)

# overwrite colors for black theme
#color["Solids"] = "#616161"

#plot aesthetics
baseSize <- 24

theme_white <- function(){
  theme_minimal(base_size = baseSize) +
    theme(
      legend.position="bottom",
      legend.title = element_blank(),
      axis.title.x=element_blank(),
      axis.ticks.x=element_blank(),
      axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5),
      #axis.text = element_text(size = theme.double.text.size),
      #legend.text=element_text(size= theme.double.text.size),
      #axis.text.x = element_text(size = 0.8*theme.double.text.size, angle = 90, hjust = 1, vjust = 0.5),
      #axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 10)),
      legend.key.height = unit(1, "cm"),
      legend.key.width = unit(1,"cm"),
      panel.background = element_rect(fill="#FFFFFF", color = NA),
      plot.background = element_rect(fill="#FFFFFF", color = NA),
      #panel.spacing = unit(1, "lines"),
      #plot.title = element_text(size = theme.double.text.size, face = "plain"),
      #strip.text.x = element_text(size = theme.double.text.size)
    )
}

```


<!-- Plots -->

```{r, echo=FALSE, include=FALSE}

g <- NULL

```



# Final Energy Electricity share


```{r, echo=FALSE, include=FALSE}

### total Electricity share

# historical data
# <- hist[hist$variable %in% unlist(vars),]

plotData <- df %>%
  filter(period >= 2010, period <= 2050,
         scenario == "WP1 NetZero",
         variable == "Final Energy|Electricity Share",
         model %in% c("IMAGE", "MEESA",  "PRIMES", "PROMETHEUS", "REMIND", "TIAM-ECN")) %>% #, "MESSAGE"
  group_by(period) %>%
  summarise_at(vars(value), list(
    Min = min,
    Mean = mean,
    Median = median,
    Max = max,
    Sd = sd,
    Q1=~quantile(., probs = 0.25),
    Q3=~quantile(., probs = 0.75)))


g[["final_energy_elec_share_total"]] <- ggplot(plotData,aes(x=period,y=Median)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_line(linewidth=1,color="black") +
    geom_ribbon(aes(ymax = Q3, ymin = Q1), alpha = 0.5, fill = "#545454") +
    geom_line(aes(y=Min),linewidth=1,color="#545454",linetype = "dashed", alpha = 0.7) +
    geom_line(aes(y=Max),linewidth=1,color="#545454",linetype = "dashed", alpha = 0.7) +
    #geom_line(data=h,linewidth=1,aes(linetype=Source)) +
    #geom_point() +
    theme_white() +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0, 0.7, by = 0.2), limits = c(0,0.7)) +
    theme(axis.title.y=element_blank())
    #ylab("Final Energy Electricity shares (%)")

if(saveCharts){
  ggsave(paste0(chartsFolder,"/svg/FE_electShare_total_NZero.svg"), g[["final_energy_elec_share_total"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
  ggsave(paste0(chartsFolder,"/png/FE_electShare_total_NZero.png"), g[["final_energy_elec_share_total"]] , device="png", width = 12, height = 8, dpi=100, units = "in")
}

g[["final_energy_elec_share_total_no_outlier"]] <- ggplot(plotData,aes(x=period,y=Median)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_line(linewidth=1,color="black") +
    geom_ribbon(aes(ymax = Q3, ymin = Q1), alpha = 0.5, fill = "#545454") +
    theme_white() +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0, 0.7, by = 0.2), limits = c(0,0.7)) +
    theme(axis.title.y=element_blank())

if(saveCharts){
  ggsave(paste0(chartsFolder,"/svg/FE_electShare_total_NZero_no_outlier.svg"), g[["final_energy_elec_share_total_no_outlier"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
  ggsave(paste0(chartsFolder,"/png/FE_electShare_total_NZero_no_outlier.png"), g[["final_energy_elec_share_total_no_outlier"]] , device="png", width = 12, height = 8, dpi=100, units = "in")
}

```


```{r, echo=FALSE, fig.width=12, fig.height=8}

plotData %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) 

  g[["final_energy_elec_share_total"]] 

```

# Final Energy Electricity share per model

```{r, echo=FALSE, include=FALSE}


plotData <- df %>%
  filter(variable == "Final Energy|Electricity Share") %>%
  filter(period >= 2010, period <= 2050,
         scenario == "WP1 NetZero")

g[["final_energy_elec_share_total_per_model"]] <- ggplot(data = plotData, aes(x = period, y = value, color = model)) +
    geom_hline(yintercept=0, color = "black", linewidth=1, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1, alpha = 0.5,linetype="dashed") +
    geom_line(linewidth = 1) +
    scale_color_manual("Models", values = c(model.colors)) +
    theme_white() +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0, 1, by = 0.2), limits = c(0,1)) +
    theme(axis.title.y=element_blank())

if(saveCharts){
  ggsave(paste0(chartsFolder,"/svg/final_energy_elec_share_total_per_model.svg"), g[["final_energy_elec_share_total_per_model"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
  ggsave(paste0(chartsFolder,"/png/final_energy_elec_share_total_per_model.png"), g[["final_energy_elec_share_total_per_model"]] , device="png", width = 12, height = 8, dpi=100, units = "in")
}

```


```{r, echo=FALSE, fig.width=12, fig.height=8}

  g[["final_energy_elec_share_total_per_model"]]

```

# Final Energy Electricity and Hydrogen share


```{r, echo=FALSE, include=FALSE}

### total Electricity and Hydrogen share

# historical data
# <- hist[hist$variable %in% unlist(vars),]

plotData <- rbind(
  df %>%
  filter(period >= 2010, period <= 2050,
         scenario == "WP1 NetZero",
         variable == "Final Energy|Electricity Share",
         model %in% c("IMAGE", "MEESA",  "PRIMES", "PROMETHEUS", "REMIND", "TIAM-ECN")) %>% #, "MESSAGE"
  group_by(period) %>%
  summarise_at(vars(value), list(
    Min = min,
    Mean = mean,
    Median = median,
    Max = max,
    Sd = sd,
    Q1=~quantile(., probs = 0.25),
    Q3=~quantile(., probs = 0.75))) %>%
    mutate(carrier = "Electricity")
  ,
  df %>%
  filter(period >= 2010, period <= 2050,
         scenario == "WP1 NetZero",
         variable == "Final Energy|Hydrogen Share",
         model %in% c("IMAGE", "MEESA",  "PRIMES", "PROMETHEUS", "REMIND", "TIAM-ECN")) %>% #, "MESSAGE"
  group_by(period) %>%
  summarise_at(vars(value), list(
    Min = min,
    Mean = mean,
    Median = median,
    Max = max,
    Sd = sd,
    Q1=~quantile(., probs = 0.25),
    Q3=~quantile(., probs = 0.75)))  %>%
    mutate(carrier = "Hydrogen")
) %>%
  mutate(carrier = factor(carrier,levels=c("Electricity","Hydrogen")))

g[["final_energy_elec_and_h2_share_total"]] <- ggplot(plotData,aes(x=period,y=Median)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_line(linewidth=1,aes(color=carrier)) +
    geom_ribbon(aes(ymax = Q3, ymin = Q1, fill = carrier), alpha = 0.5) +
    geom_line(aes(y=Min,color=carrier),linewidth=1,linetype = "dashed", alpha = 0.7) +
    geom_line(aes(y=Max,color=carrier),linewidth=1,linetype = "dashed", alpha = 0.7) +
    #geom_line(data=h,linewidth=1,aes(linetype=Source)) +
    #geom_point() +
    theme_white() +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0, 0.7, by = 0.2), limits = c(0,0.7)) +
    theme(axis.title.y=element_blank()) +
    scale_fill_manual(values = c("Electricity"="#545454","Hydrogen"="#007c7d")) +
    scale_color_manual(values = c("Electricity"="#545454","Hydrogen"="#007c7d")) +
    guides(color = FALSE)
      
if(saveCharts){
  ggsave(paste0(chartsFolder,"/svg/FE_elect_and_H2_Share_total_NZero.svg"), g[["final_energy_elec_and_h2_share_total"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
  ggsave(paste0(chartsFolder,"/png/FE_elect_and_H2_Share_total_NZero.png"), g[["final_energy_elec_and_h2_share_total"]] , device="png", width = 12, height = 8, dpi=100, units = "in")
}

g[["final_energy_elec_and_h2_share_total_no_outlier"]] <- ggplot(plotData,aes(x=period,y=Median)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_line(linewidth=1,aes(color=carrier)) +
    geom_ribbon(aes(ymax = Q3, ymin = Q1, fill = carrier), alpha = 0.5) +
    theme_white() +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0, 0.7, by = 0.2), limits = c(0,0.7)) +
    theme(axis.title.y=element_blank()) +
    scale_fill_manual(values = c("Electricity"="#545454","Hydrogen"="#007c7d")) +
    scale_color_manual(values = c("Electricity"="#545454","Hydrogen"="#007c7d")) +
    guides(color = FALSE)
      
if(saveCharts){
  ggsave(paste0(chartsFolder,"/svg/FE_elect_and_H2_Share_total_NZero_no_outlier.svg"), g[["final_energy_elec_and_h2_share_total_no_outlier"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
  ggsave(paste0(chartsFolder,"/png/FE_elect_and_H2_Share_total_NZero_no_outlier.png"), g[["final_energy_elec_and_h2_share_total_no_outlier"]] , device="png", width = 12, height = 8, dpi=100, units = "in")
}

```


```{r, echo=FALSE, fig.width=12, fig.height=8}


plotData %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) 

  g[["final_energy_elec_and_h2_share_total"]] 

```


# Final Energy Hydrogen share per model

```{r, echo=FALSE, include=FALSE}


plotData <- df %>%
  filter(variable == "Final Energy|Hydrogen Share") %>%
  filter(period >= 2010, period <= 2050,
         scenario == "WP1 NetZero")

g[["final_energy_h2_share_total_per_model"]] <- ggplot(data = plotData, aes(x = period, y = value, color = model)) +
    geom_hline(yintercept=0, color = "black", linewidth=1, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1, alpha = 0.5,linetype="dashed") +
    geom_line(linewidth = 1) +
    scale_color_manual("Models", values = c(model.colors)) +
    theme_white() +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0, 1, by = 0.2), limits = c(0,1)) +
    theme(axis.title.y=element_blank())

if(saveCharts){
  ggsave(paste0(chartsFolder,"/svg/final_energy_h2_share_total_per_model.svg"), g[["final_energy_h2_share_total_per_model"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
  ggsave(paste0(chartsFolder,"/png/final_energy_h2_share_total_per_model.png"), g[["final_energy_h2_share_total_per_model"]] , device="png", width = 12, height = 8, dpi=100, units = "in")
}

```


```{r, echo=FALSE, fig.width=12, fig.height=8}

  g[["final_energy_h2_share_total_per_model"]]

```


# Power sector Emissions


```{r, echo=FALSE, include=FALSE}

### total Electricity share

# historical data
# <- hist[hist$variable %in% unlist(vars),]

plotData <- df %>%
  filter(period >= 2010, period <= 2050,
         scenario == "WP1 NetZero",
         variable == "Emissions|CO2|Energy|Supply|Electricity",
         model %in% c("IMAGE", "LIMES", "MEESA", "OSEMBE", "PRIMES", "PROMETHEUS", "REMIND", "TIAM-ECN", "WITCH")) %>%
  group_by(period) %>%
  summarise_at(vars(value), list(
    Min = min,
    Mean = mean,
    Median = median,
    Max = max,
    Sd = sd,
    Q1=~quantile(., probs = 0.25),
    Q3=~quantile(., probs = 0.75)))


g[["power_sector_emissions"]] <- ggplot(plotData,aes(x=period,y=Median)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_line(linewidth=1,color="black") +
    geom_ribbon(aes(ymax = Q3, ymin = Q1), alpha = 0.5, fill = "#545454") +
    geom_line(aes(y=Min),linewidth=1,color="#545454",linetype = "dashed", alpha = 0.7) +
    geom_line(aes(y=Max),linewidth=1,color="#545454",linetype = "dashed", alpha = 0.7) +
    #geom_line(data=h,linewidth=1,aes(linetype=Source)) +
    #geom_point() +
    theme_white() +
    ylab(expression(paste("Mt ", CO[2],"/yr")))

if(saveCharts){
  ggsave(paste0(chartsFolder,"/svg/power_sector_emissions.svg"), g[["power_sector_emissions"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
  ggsave(paste0(chartsFolder,"/png/power_sector_emissions.png"), g[["power_sector_emissions"]] , device="png", width = 12, height = 8, dpi=100, units = "in")
}

g[["power_sector_emissions_no_outlier"]] <- ggplot(plotData,aes(x=period,y=Median)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_line(linewidth=1,color="black") +
    geom_ribbon(aes(ymax = Q3, ymin = Q1), alpha = 0.5, fill = "#545454") +
    theme_white() +
    ylab(expression(paste("Mt ", CO[2],"/yr")))

if(saveCharts){
  ggsave(paste0(chartsFolder,"/svg/power_sector_emissions_no_outlier.svg"), g[["power_sector_emissions_no_outlier"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
  ggsave(paste0(chartsFolder,"/png/power_sector_emissions_no_outlier.png"), g[["power_sector_emissions_no_outlier"]] , device="png", width = 12, height = 8, dpi=100, units = "in")
}


```


```{r, echo=FALSE, fig.width=12, fig.height=8}


plotData %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) 

  g[["power_sector_emissions"]] 

```


# Power sector Emissions per model

```{r, echo=FALSE, include=FALSE}


plotData <- df %>%
  filter(variable == "Emissions|CO2|Energy|Supply|Electricity") %>%
  filter(period >= 2010, period <= 2050,
         scenario == "WP1 NetZero")

g[["power_sector_emissions_per_model"]] <- ggplot(data = plotData, aes(x = period, y = value, color = model)) +
    geom_hline(yintercept=0, color = "black", linewidth=1, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1, alpha = 0.5,linetype="dashed") +
    geom_line(linewidth = 1) +
    scale_color_manual("Models", values = c(model.colors)) +
    theme_white() +
    ylab(as.character(unique(plotData$unit)))

if(saveCharts){
  ggsave(paste0(chartsFolder,"/svg/power_sector_emissions_per_model.svg"), g[["power_sector_emissions_per_model"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
  ggsave(paste0(chartsFolder,"/png/power_sector_emissions_per_model.png"), g[["power_sector_emissions_per_model"]] , device="png", width = 12, height = 8, dpi=100, units = "in")
}

```


```{r, echo=FALSE, fig.width=12, fig.height=8}

  g[["power_sector_emissions_per_model"]]

```

# Wind and Solar generation


```{r, echo=FALSE, include=FALSE}

### total Electricity share

# historical data
# <- hist[hist$variable %in% unlist(vars),]

plotData <- bind_rows(
  df %>%
    filter(
      period %in% seq(2010,2050,5),
      scenario == "WP1 NetZero",
      variable %in% c("Secondary Energy|Electricity|Solar|PV"),
      model == "OSeMBE") %>%
  mutate(variable = "Secondary Energy|Electricity|Solar")
  ,
  df %>%
    filter(
      period %in% seq(2010,2050,5),
      scenario == "WP1 NetZero",
      variable %in% c("Secondary Energy|Electricity|Solar","Secondary Energy|Electricity|Wind"),
      model %in% c("IMAGE", "LIMES", "MEESA", "OSeMBE", "PRIMES", "PROMETHEUS", "REMIND", "TIAM-ECN", "WITCH"))
  ) %>%
  group_by(model,period) %>%
  summarize(value = sum(value)) %>%
  mutate(value = value*277.7777778) %>% # EJ 2 TWh
  group_by(period) %>%
  summarise_at(vars(value), list(
    Min = min,
    Mean = mean,
    Median = median,
    Max = max,
    Sd = sd,
    Q1=~quantile(., probs = 0.25),
    Q3=~quantile(., probs = 0.75)))


g[["Wind_and_Solar_generation"]] <- ggplot(plotData,aes(x=period,y=Median)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_line(linewidth=1,color="black") +
    geom_ribbon(aes(ymax = Q3, ymin = Q1), alpha = 0.5, fill = "#545454") +
    geom_line(aes(y=Min),linewidth=1,color="#545454",linetype = "dashed", alpha = 0.7) +
    geom_line(aes(y=Max),linewidth=1,color="#545454",linetype = "dashed", alpha = 0.7) +
    #geom_line(data=h,linewidth=1,aes(linetype=Source)) +
    #geom_point() +
    theme_white() +
    #scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0, 1, by = 0.2), limits = c(0,1)) +
    ylab("TWh/yr")

if(saveCharts){
  ggsave(paste0(chartsFolder,"/svg/Wind_and_Solar_generation.svg"), g[["Wind_and_Solar_generation"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
  ggsave(paste0(chartsFolder,"/png/Wind_and_Solar_generation.png"), g[["Wind_and_Solar_generation"]] , device="png", width = 12, height = 8, dpi=100, units = "in")
}


g[["Wind_and_Solar_generation_no_outlier"]] <- ggplot(plotData,aes(x=period,y=Median)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_line(linewidth=1,color="black") +
    geom_ribbon(aes(ymax = Q3, ymin = Q1), alpha = 0.5, fill = "#545454") +
    #geom_line(data=h,linewidth=1,aes(linetype=Source)) +
    #geom_point() +
    theme_white() +
    #scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0, 1, by = 0.2), limits = c(0,1)) +
    ylab("TWh/yr")

if(saveCharts){
  ggsave(paste0(chartsFolder,"/svg/Wind_and_Solar_generation_no_outlier.svg"), g[["Wind_and_Solar_generation_no_outlier"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
  ggsave(paste0(chartsFolder,"/png/Wind_and_Solar_generation_no_outlier.png"), g[["Wind_and_Solar_generation_no_outlier"]] , device="png", width = 12, height = 8, dpi=100, units = "in")
}

```


```{r, echo=FALSE, fig.width=12, fig.height=8}


plotData %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) 

  g[["Wind_and_Solar_generation"]] 

```



# Wind and Solar generation per model

```{r, echo=FALSE, include=FALSE}

plotData <- bind_rows(
  df %>%
    filter(
      period %in% seq(2010,2050,5),
      scenario == "WP1 NetZero",
      variable %in% c("Secondary Energy|Electricity|Solar|PV"),
      model == "OSeMBE") %>%
  mutate(variable = "Secondary Energy|Electricity|Solar")
  ,
  df %>%
    filter(
      period %in% seq(2010,2050,5),
      scenario == "WP1 NetZero",
      variable %in% c("Secondary Energy|Electricity|Solar","Secondary Energy|Electricity|Wind"),
      model %in% c("IMAGE", "LIMES", "MEESA", "OSeMBE", "PRIMES", "PROMETHEUS", "REMIND", "TIAM-ECN", "WITCH"))
  ) %>%
  group_by(model,period) %>%
  summarize(value = sum(value)) %>%
  mutate(value = value*277.7777778)


g[["Wind_and_Solar_generation_per_model"]] <- ggplot(data = plotData, aes(x = period, y = value, color = model)) +
    geom_hline(yintercept=0, color = "black", linewidth=1, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1, alpha = 0.5,linetype="dashed") +
    geom_line(linewidth = 1) +
    scale_color_manual("Models", values = c(model.colors)) +
    theme_white() +
    ylab("TWh/yr")

if(saveCharts){
  ggsave(paste0(chartsFolder,"/svg/Wind_and_Solar_generation_per_model.svg"), g[["Wind_and_Solar_generation_per_model"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
  ggsave(paste0(chartsFolder,"/png/Wind_and_Solar_generation_per_model.png"), g[["Wind_and_Solar_generation_per_model"]] , device="png", width = 12, height = 8, dpi=100, units = "in")
}

```


```{r, echo=FALSE, fig.width=12, fig.height=8}

  g[["Wind_and_Solar_generation_per_model"]]

```

## VRE share

```{r, echo=FALSE, include=FALSE}

plotData <- left_join(
  bind_rows(
    df %>%
      filter(
        period %in% seq(2010,2050,5),
        scenario == "WP1 NetZero",
        variable %in% c("Secondary Energy|Electricity|Solar|PV"),
        model == "OSeMBE") %>%
    mutate(variable = "Secondary Energy|Electricity|Solar")
    ,
    df %>%
      filter(
        period %in% seq(2010,2050,5),
        scenario == "WP1 NetZero",
        variable %in% c("Secondary Energy|Electricity|Solar","Secondary Energy|Electricity|Wind"),
        model %in% c("IMAGE", "LIMES", "MEESA", "OSeMBE", "PRIMES", "PROMETHEUS", "REMIND", "TIAM-ECN", "WITCH"))
    ) %>%
    group_by(model,period) %>%
    summarize(value = sum(value)) %>%
    mutate(VRE = value) %>%
    select(model,period,VRE)
  ,
  df %>%
      filter(
        period %in% seq(2010,2050,5),
        scenario == "WP1 NetZero",
        variable %in% c("Secondary Energy|Electricity")) %>%
    select(model,period,value) %>%
    mutate(Total = value) %>%
    select(model,period,Total)
  ,
  by = join_by(model == model, period == period)
  ) %>%
  mutate(VRE_share = VRE/Total) %>%
  group_by(period) %>%
  summarise_at(vars(VRE_share), list(
    Min = min,
    Mean = mean,
    Median = median,
    Max = max,
    Sd = sd,
    Q1=~quantile(., probs = 0.25),
    Q3=~quantile(., probs = 0.75)))

g[["VRE_share"]] <- ggplot(plotData,aes(x=period,y=Median)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_line(linewidth=1,color="black") +
    geom_ribbon(aes(ymax = Q3, ymin = Q1), alpha = 0.5, fill = "#545454") +
    geom_line(aes(y=Min),linewidth=1,color="#545454",linetype = "dashed", alpha = 0.7) +
    geom_line(aes(y=Max),linewidth=1,color="#545454",linetype = "dashed", alpha = 0.7) +
    #geom_line(data=h,linewidth=1,aes(linetype=Source)) +
    #geom_point() +
    theme_white() +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0, 1, by = 0.2), limits = c(0,1)) +
    theme(axis.title.y=element_blank())

if(saveCharts){
  ggsave(paste0(chartsFolder,"/svg/VRE_share.svg"), g[["VRE_share"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
  ggsave(paste0(chartsFolder,"/png/VRE_share.png"), g[["VRE_share"]] , device="png", width = 12, height = 8, dpi=100, units = "in")
}

g[["VRE_share_no_outlier"]] <- ggplot(plotData,aes(x=period,y=Median)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_line(linewidth=1,color="black") +
    geom_ribbon(aes(ymax = Q3, ymin = Q1), alpha = 0.5, fill = "#545454") +
    theme_white() +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0, 1, by = 0.2), limits = c(0,1)) +
    theme(axis.title.y=element_blank())

if(saveCharts){
  ggsave(paste0(chartsFolder,"/svg/VRE_share_no_outlier.svg"), g[["VRE_share_no_outlier"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
  ggsave(paste0(chartsFolder,"/png/VRE_share_no_outlier.png"), g[["VRE_share_no_outlier"]] , device="png", width = 12, height = 8, dpi=100, units = "in")
}

```


```{r, echo=FALSE, fig.width=12, fig.height=8}


plotData %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) 

  g[["VRE_share"]]

```



# Wind and Solar generation per model

```{r, echo=FALSE, include=FALSE}

plotData <- left_join(
    bind_rows(
      df %>%
        filter(
          period %in% seq(2010,2050,5),
          scenario == "WP1 NetZero",
          variable %in% c("Secondary Energy|Electricity|Solar|PV"),
          model == "OSeMBE") %>%
      mutate(variable = "Secondary Energy|Electricity|Solar")
      ,
      df %>%
        filter(
          period %in% seq(2010,2050,5),
          scenario == "WP1 NetZero",
          variable %in% c("Secondary Energy|Electricity|Solar","Secondary Energy|Electricity|Wind"),
          model %in% c("IMAGE", "LIMES", "MEESA", "OSeMBE", "PRIMES", "PROMETHEUS", "REMIND", "TIAM-ECN", "WITCH"))
      ) %>%
      group_by(model,period) %>%
      summarize(value = sum(value)) %>%
      mutate(VRE = value) %>%
      select(model,period,VRE)
    ,
    df %>%
        filter(
          period %in% seq(2010,2050,5),
          scenario == "WP1 NetZero",
          variable %in% c("Secondary Energy|Electricity")) %>%
      select(model,period,value) %>%
      mutate(Total = value) %>%
      select(model,period,Total)
    ,
    by = join_by(model == model, period == period)
  ) %>%
  mutate(VRE_share = VRE/Total)


g[["VRE_share_per_model"]] <- ggplot(data = plotData, aes(x = period, y = VRE_share, color = model)) +
    geom_hline(yintercept=0, color = "black", linewidth=1, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1, alpha = 0.5,linetype="dashed") +
    geom_line(linewidth = 1) +
    scale_color_manual("Models", values = c(model.colors)) +
    theme_white() +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0, 1, by = 0.2), limits = c(0,1)) +
    theme(axis.title.y=element_blank())

if(saveCharts){
  ggsave(paste0(chartsFolder,"/svg/VRE_share_per_model.svg"), g[["VRE_share_per_model"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
  ggsave(paste0(chartsFolder,"/png/VRE_share_per_model.png"), g[["VRE_share_per_model"]] , device="png", width = 12, height = 8, dpi=100, units = "in")
}

```


```{r, echo=FALSE, fig.width=12, fig.height=8}

  g[["VRE_share_per_model"]]

```


# GHG Emission reductions

(shifted to LULUCF national accounting)

```{r, echo=FALSE}

### GHG Emissions

currData <- NULL

for (m in unique(df$model)){
  
  currDf <- df %>% filter(model == m) %>%
    group_by(variable) %>%
    filter(!all(value==0))

  if(!any(c("Emissions|CO2", "Emissions|Kyoto Gases") %in% unique(currDf$variable))){
    print(paste0(m , " - skipped.")) 
    next
  }
  
  if(any(c("Euro-Calliope","LIMES","OSeMBE") %in% unique(currDf$model))){
    print(paste0(m , " - skipped.")) 
    next
  }
  
  altData <- NULL
  # Emissions|Kyoto Gases|AFOLU|Land (est.)
  if("Emissions|Kyoto Gases|AFOLU|Land" %in% unique(currDf$variable)){ # if model report variable
    altData <- rbind(
      altData,
      currDf %>%
        filter(variable == "Emissions|Kyoto Gases|AFOLU|Land") %>%
        mutate(variable = "Emissions|Kyoto Gases|AFOLU|Land (est.)")
    )
  } else if( all(c("Emissions|CO2|AFOLU|Land", "Emissions|CH4|AFOLU|Land", "Emissions|N2O|AFOLU|Land") %in% unique(currDf$variable) )){
    print(paste0(m , " - estimates `Emissions|Kyoto Gases|AFOLU|Land` from `Emissions|CO2, CH4 and N2o|AFOLU|Land` variables.")) 
    altData <- calc_addVariable(currDf, "`Emissions|Kyoto Gases|AFOLU|Land (est.)`" = "`Emissions|CO2|AFOLU|Land` + 28*`Emissions|CH4|AFOLU|Land` + 265/1000 * `Emissions|N2O|AFOLU|Land`", units = "Mt CO2e/yr", completeMissing=T, only.new = TRUE) 
  } else if( all(c("Carbon Removal|Land Use", "Emissions|CH4|AFOLU|Land", "Emissions|N2O|AFOLU|Land") %in% unique(currDf$variable) )){
    print(paste0(m , " - estimates `Emissions|Kyoto Gases|AFOLU|Land` from `Carbon Removal|Land Use` and `Emissions|CH4 and N2o|AFOLU|Land` variables."))
    if(all(currDf %>% filter(variable == "Carbon Removal|Land Use") %>% pull(value) >= 0)){
      altData <- rbind(
        altData,
        calc_addVariable(currDf, "`Emissions|Kyoto Gases|AFOLU|Land (est.)`" = "-`Carbon Removal|Land Use` + 28*`Emissions|CH4|AFOLU|Land` + 265/1000 * `Emissions|N2O|AFOLU|Land`", units = "Mt CO2e/yr", completeMissing=T, only.new = TRUE) 
      )
    } else {
      altData <- rbind(
        altData,
        calc_addVariable(currDf, "`Emissions|Kyoto Gases|AFOLU|Land (est.)`" = "`Carbon Removal|Land Use` + 28*`Emissions|CH4|AFOLU|Land` + 265/1000 * `Emissions|N2O|AFOLU|Land`", units = "Mt CO2e/yr", completeMissing=T, only.new = TRUE) 
      )
    }
  } else {
    print(paste0(m , " - assuming zero LULUCF emissions as the model does not report the necessary variables."))
    altData <- rbind(
      altData,
      currDf %>% 
        filter(variable == "Emissions|CO2", scenario == "WP1 NetZero") %>%
        mutate(variable = "Emissions|Kyoto Gases|AFOLU|Land (est.)",
               value = 0,
               unit = "Mt CO2e/yr")
      )
  }
  
  # Emissions|Kyoto Gases (est.)
  if("Emissions|Kyoto Gases" %in% unique(currDf$variable)){
    altData <- rbind(
      altData,
      calc_addVariable(currDf, "`Emissions|Kyoto Gases (est.)`" = "`Emissions|Kyoto Gases`", units = "Mt CO2e/yr", completeMissing=T, only.new = TRUE) 
    )
  } else {
    print(paste0(m , " - scaling CO2 emissions to estimate GHG due to the lack of reporting the `Emissions|Kyoto Gases` variable."))
    if(unique(currDf$region) == "EU27 (*)"){
      factor <- 3125 / # 3125 = 2020 Emissions with LULUCF and with intra-EU aviation
        currDf %>% filter(variable == "Emissions|CO2", period == "2020", scenario == "WP1 NetZero") %>% pull(value)
    } else if(unique(currDf$region) == "EU27 & UK (*)"){
      factor <- (3125 + 405.5 + 14.5 + 6.1) / # ???? = 2020 Emissions with LULUCF and with international transport
        currDf %>% filter(variable == "Emissions|CO2", period == "2020", scenario == "WP1 NetZero") %>% pull(value)
    }
    altData <- rbind(
      altData, 
      currDf %>%
        filter(variable == "Emissions|CO2") %>%
                mutate(value = value * factor,
                       variable = "Emissions|Kyoto Gases (est.)",
                       unit = "Mt CO2e/yr")
    )
  }
  
  # Emissions|Kyoto|w/o LULUCF (est.)
  altData <- calc_addVariable(altData, "`Emissions|Kyoto|w/o LULUCF (est.)`" = "`Emissions|Kyoto Gases (est.)` - `Emissions|Kyoto Gases|AFOLU|Land (est.)`", units = "Mt CO2e/yr", completeMissing=T) 
  
  # Emissions|Kyoto|AFOLU|Land (shifted to national accounting)
  altData <- rbind(
      altData,
      left_join(
        altData %>%
          filter(variable == "Emissions|Kyoto Gases|AFOLU|Land (est.)", period == 2020) %>%
          mutate(shift2020= -244 - value) %>%
          ungroup() %>%
          select(scenario,region,shift2020)
        ,
        altData %>%
          filter(variable == "Emissions|Kyoto Gases|AFOLU|Land (est.)")
        ,
        by = join_by(scenario,region)
      ) %>%
        mutate(value = value + shift2020) %>%
        mutate(variable = "Emissions|Kyoto|AFOLU|Land (shifted to national accounting)") %>%
        ungroup() %>%
        select(model, scenario, region, variable, unit, period, value)
  )
  
  # Emissions|Kyoto (shifted to national accounting)
  altData <- rbind(
      altData,
      left_join(
        altData %>%
          filter(variable == "Emissions|Kyoto|AFOLU|Land (shifted to national accounting)") %>%
          mutate(land = value) %>%
          ungroup() %>%
          select(model, scenario, region, period, land)
        ,
        altData %>%
          filter(variable == "Emissions|Kyoto|w/o LULUCF (est.)")
        ,
        by = join_by(model, scenario, region, period)
      ) %>%
        mutate(value = value + land) %>%
        mutate(variable = "Emissions|Kyoto (shifted to national accounting)") %>%
        ungroup() %>%
        select(model, scenario, region, variable, unit, period, value)
  )
  
  currData <- rbind(currData,altData)
  
}


#Emissions Reduction

if(unique(currDf$region) == "EU27 (*)"){
  emi1990 <- 4713
} else if(unique(currDf$region) == "EU27 & UK (*)"){
  emi1990 <- 4713 + 812.4 
}
print(paste0("Using ", emi1990, " MtCO2eq, for 1990 emissions from ", unique(currDf$region), ", to calculate emission reductions."))

print(paste0("Models included in results: ", toString(unique(currData$model))))
#2015 reductions provide a reference 1990 calculated emission of 4726 Mt/CO2eq, from 2040 S1 is 4777, from 2040 S2 is 4567 and from 2040 S3 is 4450.
#For our scenarios, all emission reductions were calculated using the net GHG emissions without international transport and using the 1990 reference emissions with LULUCF and intra-EU aviation only (4713 Mt CO2e).
#region , variable , unit , period , value
#EU27 , Emissions with LULUCF and with intra-EU aviation , Gg CO2 equivalent , 1990 , 4712.877
#EU27 , Emissions with LULUCF and with international transport , Gg CO2 equivalent , 1990 , 4814.415
#EU27 , Emissions without LULUCF and with intra-EU aviation , Gg CO2 equivalent , 1990 , 4921.672
#EU27 , Emissions without LULUCF and with international transport , Gg CO2 equivalent , 1990 , 5023.21
#EU27 , Emissions with LULUCF and without international transport , Gg CO2 equivalent , 1990 , 4658.202

plotData <- currData %>%
  filter(variable == "Emissions|Kyoto (shifted to national accounting)") %>%
  mutate(value =-1*( 1 - (value / emi1990)),
         variable = "Emissions Reduction",
         unit = "%") %>%
  filter(period >= 2010, period <= 2050,
         scenario == "WP1 NetZero") %>%
  group_by(period) %>%
  summarise_at(vars(value), list(
    Min = min,
    Mean = mean,
    Median = median,
    Max = max,
    Sd = sd,
    Q1=~quantile(., probs = 0.25, na.rm=TRUE),
    Q3=~quantile(., probs = 0.75, na.rm=TRUE)))

g[["ghg_emissions_reductions_NZero"]] <- ggplot(plotData,aes(x=period,y=Median)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_line(linewidth=1,color="black") +
    geom_ribbon(aes(ymax = Q3, ymin = Q1), alpha = 0.5, fill = "#545454") +
    geom_line(aes(y=Min),linewidth=1,color="#545454",linetype = "dashed", alpha = 0.7) +
    geom_line(aes(y=Max),linewidth=1,color="#545454",linetype = "dashed", alpha = 0.7) +
    #geom_line(data=h,linewidth=1,aes(linetype=Source)) +
    #geom_point() +
    theme_white() +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(-1, 0, by = 0.2)) +
    theme(axis.title.y=element_blank())

if(saveCharts){
  ggsave(paste0(chartsFolder,"/svg/ghg_emissions_reductions_NZero.svg"), g[["ghg_emissions_reductions_NZero"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
  ggsave(paste0(chartsFolder,"/png/ghg_emissions_reductions_NZero.png"), g[["ghg_emissions_reductions_NZero"]] , device="png", width = 12, height = 8, dpi=100, units = "in")
}

g[["ghg_emissions_reductions_NZero_no_outlier"]] <- ggplot(plotData,aes(x=period,y=Median)) +
    geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") +
    geom_line(linewidth=1,color="black") +
    geom_ribbon(aes(ymax = Q3, ymin = Q1), alpha = 0.5, fill = "#545454") +
    theme_white() +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(-1, 0, by = 0.2)) +
    theme(axis.title.y=element_blank())

if(saveCharts){
  ggsave(paste0(chartsFolder,"/svg/ghg_emissions_reductions_NZero_no_outlier.svg"), g[["ghg_emissions_reductions_NZero_no_outlier"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
  ggsave(paste0(chartsFolder,"/png/ghg_emissions_reductions_NZero_no_outlier.png"), g[["ghg_emissions_reductions_NZero_no_outlier"]] , device="png", width = 12, height = 8, dpi=100, units = "in")
}


```


```{r, echo=FALSE, fig.width=12, fig.height=8}

plotData %>%
  kbl() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) 

  g[["ghg_emissions_reductions_NZero"]]

```


# GHG Emission reductions per model

(shifted to LULUCF national accounting)

```{r, echo=FALSE, include=FALSE}

plotData <- currData %>%
  filter(variable == "Emissions|Kyoto (shifted to national accounting)") %>%
  mutate(value =-1*( 1 - (value / emi1990)),
         variable = "Emissions Reduction",
         unit = "%") %>%
  filter(period >= 2010, period <= 2050,
         scenario == "WP1 NetZero")

g[["ghg_emissions_reductions_NZero_per_model"]] <- ggplot(data = plotData, aes(x = period, y = value, color = model)) +
    geom_hline(yintercept=0, color = "black", linewidth=1, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1, alpha = 0.5,linetype="dashed") +
    geom_line(linewidth = 1) +
    scale_color_manual("Models", values = c(model.colors)) +
    theme_white() +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(-1, 0, by = 0.2)) +
    theme(axis.title.y=element_blank())

if(saveCharts){
  ggsave(paste0(chartsFolder,"/svg/ghg_emissions_reductions_NZero_per_model.svg"), g[["ghg_emissions_reductions_NZero_per_model"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
  ggsave(paste0(chartsFolder,"/png/ghg_emissions_reductions_NZero_per_model.png"), g[["ghg_emissions_reductions_NZero_per_model"]] , device="png", width = 12, height = 8, dpi=100, units = "in")
}

```


```{r, echo=FALSE, fig.width=12, fig.height=8}

#plotData %>%
#  kbl() %>%
#  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) 

  g[["ghg_emissions_reductions_NZero_per_model"]]

```



# GHG Emissions per model

(shifted to LULUCF national accounting)

```{r, echo=FALSE, include=FALSE}

plotData <- currData %>%
  filter(variable == "Emissions|Kyoto (shifted to national accounting)") %>%
  filter(period >= 2010, period <= 2050,
         scenario == "WP1 NetZero")

g[["ghg_emissions_per_model"]] <- ggplot(data = plotData, aes(x = period, y = value, color = model)) +
    geom_hline(yintercept=0, color = "black", linewidth=1, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1, alpha = 0.5,linetype="dashed") +
    geom_line(linewidth = 1) +
    scale_color_manual("Models", values = c(model.colors)) +
    theme_white() +
    ylab(as.character(unique(plotData$unit)))

if(saveCharts){
  ggsave(paste0(chartsFolder,"/svg/ghg_emissions_per_model.svg"), g[["ghg_emissions_per_model"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
  ggsave(paste0(chartsFolder,"/png/ghg_emissions_per_model.png"), g[["ghg_emissions_per_model"]] , device="png", width = 12, height = 8, dpi=100, units = "in")
}

```


```{r, echo=FALSE, fig.width=12, fig.height=8}

#plotData %>%
#  kbl() %>%
#  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) 

  g[["ghg_emissions_per_model"]]

```


# LULUCF Emissions per model

(shifted to LULUCF national accounting)

```{r, echo=FALSE, include=FALSE}

plotData <- currData %>%
  filter(variable == "Emissions|Kyoto|AFOLU|Land (shifted to national accounting)") %>%
  filter(period >= 2010, period <= 2050,
         scenario == "WP1 NetZero")

g[["lulucf_emissions_per_model"]] <- ggplot(data = plotData, aes(x = period, y = value, color = model)) +
    geom_hline(yintercept=0, color = "black", linewidth=1, alpha = 0.5) +
    geom_vline(xintercept=2020, color = "black", linewidth=1, alpha = 0.5,linetype="dashed") +
    geom_line(linewidth = 1) +
    scale_color_manual("Models", values = c(model.colors)) +
    theme_white() +
    ylab(as.character(unique(plotData$unit)))

if(saveCharts){
  ggsave(paste0(chartsFolder,"/svg/lulucf_emissions_per_model.svg"), g[["lulucf_emissions_per_model"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
  ggsave(paste0(chartsFolder,"/png/lulucf_emissions_per_model.png"), g[["lulucf_emissions_per_model"]] , device="png", width = 12, height = 8, dpi=100, units = "in")
}

```


```{r, echo=FALSE, fig.width=12, fig.height=8}

#plotData %>%
#  kbl() %>%
#  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) 

  g[["lulucf_emissions_per_model"]]

```

<!-- ```{r, echo=FALSE, include=FALSE} -->

<!-- plotData <- read.csv2("emissions_reductions_robert_v2.csv",check.names=FALSE,stringsAsFactors=FALSE) %>% -->
<!--   gather(period, value, -c(1)) %>% -->
<!--   mutate_at(c('value',"period"), as.numeric) %>% -->
<!--   filter(period %in% seq(2010,2050,5), -->
<!--          model %in% c("IMAGE", "PRIMES", "PROMETHEUS", "REMIND", "TIAM-ECN", "WITCH")) -->

<!-- plotDataStat <- plotData %>% -->
<!--   group_by(period) %>% -->
<!--   summarise_at(vars(value), list( -->
<!--     Min = min, -->
<!--     Mean = mean, -->
<!--     Median = median, -->
<!--     Max = max, -->
<!--     Sd = sd, -->
<!--     Q1=~quantile(., probs = 0.25, na.rm=TRUE), -->
<!--     Q3=~quantile(., probs = 0.75, na.rm=TRUE))) -->


<!-- g[["GHG_Emissions_reductions"]] <- ggplot(plotData,aes(x=period)) + -->
<!--     geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) + -->
<!--     geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") + -->
<!--     geom_line(linewidth=1,aes(y=value,group=model),color="#545454",alpha=0.5) + -->
<!--     geom_line(data=plotDataStat,aes(y=Median),linewidth=1,color="black") + -->
<!--     geom_ribbon(data=plotDataStat,aes(ymax = Q3, ymin = Q1), alpha = 0.5, fill = "#545454") + -->
<!--     theme_white() + -->
<!--     scale_y_continuous(labels = scales::percent_format(accuracy = 1),breaks = seq(-1, 0, by = 0.2)) + #, breaks = seq(-1, 0, by = 0.2), limits = c(0,-1)) + -->
<!--     theme(axis.title.y=element_blank()) -->
<!--     #ylab("Final Energy Electricity shares (%)") -->

<!-- if(saveCharts){ -->
<!--   ggsave(paste0(chartsFolder,"/svg/GHG_Emissions_reductions.svg"), g[["GHG_Emissions_reductions"]] , device="svg", width = 12, height = 8, dpi=100, units = "in") -->
<!--   ggsave(paste0(chartsFolder,"/png/GHG_Emissions_reductions.png"), g[["GHG_Emissions_reductions"]] , device="png", width = 12, height = 8, dpi=100, units = "in") -->
<!-- } -->

<!-- g[["GHG_Emissions_reductions_v2"]] <- ggplot(plotData,aes(x=period)) + -->
<!--     geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) + -->
<!--     geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") + -->
<!--     #geom_line(linewidth=1,aes(y=value,group=model),color="#545454",alpha=0.5) + -->
<!--     geom_line(data=plotDataStat,aes(y=Median),linewidth=1,color="black") + -->
<!--     geom_ribbon(data=plotDataStat,aes(ymax = Q3, ymin = Q1), alpha = 0.5, fill = "#545454") + -->
<!--     theme_white() + -->
<!--     scale_y_continuous(labels = scales::percent_format(accuracy = 1),breaks = seq(-1, 0, by = 0.2)) + #, breaks = seq(-1, 0, by = 0.2), limits = c(0,-1)) + -->
<!--     theme(axis.title.y=element_blank()) -->
<!--     #ylab("Final Energy Electricity shares (%)") -->

<!-- if(saveCharts){ -->
<!--   ggsave(paste0(chartsFolder,"/svg/GHG_Emissions_reductions_v2.svg"), g[["GHG_Emissions_reductions_v2"]] , device="svg", width = 12, height = 8, dpi=100, units = "in") -->
<!--   ggsave(paste0(chartsFolder,"/png/GHG_Emissions_reductions_v2.png"), g[["GHG_Emissions_reductions_v2"]] , device="png", width = 12, height = 8, dpi=100, units = "in") -->
<!-- } -->

<!-- g[["GHG_Emissions_reductions_v3"]] <- ggplot(plotData %>% filter(period >= 2025),aes(x=period)) + -->
<!--     geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) + -->
<!--     #geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") + -->
<!--     geom_line(linewidth=1,aes(y=value,group=model),color="#545454",alpha=0.5) + -->
<!--     geom_line(data=plotDataStat %>% filter(period >= 2025),aes(y=Median),linewidth=1,color="black") + -->
<!--     geom_ribbon(data=plotDataStat %>% filter(period >= 2025),aes(ymax = Q3, ymin = Q1), alpha = 0.5, fill = "#545454") + -->
<!--     theme_white() + -->
<!--     scale_y_continuous(labels = scales::percent_format(accuracy = 1),breaks = seq(-1, 0, by = 0.2)) + #, breaks = seq(-1, 0, by = 0.2), limits = c(0,-1)) + -->
<!--     theme(axis.title.y=element_blank()) -->
<!--     #ylab("Final Energy Electricity shares (%)") -->

<!-- if(saveCharts){ -->
<!--   ggsave(paste0(chartsFolder,"/svg/GHG_Emissions_reductions_v3.svg"), g[["GHG_Emissions_reductions_v3"]] , device="svg", width = 12, height = 8, dpi=100, units = "in") -->
<!--   ggsave(paste0(chartsFolder,"/png/GHG_Emissions_reductions_v3.png"), g[["GHG_Emissions_reductions_v3"]] , device="png", width = 12, height = 8, dpi=100, units = "in") -->
<!-- } -->

<!-- ``` -->


<!-- ```{r, echo=FALSE, fig.width=12, fig.height=8} -->


<!-- plotDataStat %>% -->
<!--   kbl() %>% -->
<!--   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))  -->

<!--   g[["GHG_Emissions_reductions_v3"]]  -->

<!-- ``` -->


<!-- ## Exogenous Carbon Capture - average -->

<!-- ```{r, echo=FALSE, include=FALSE} -->

<!-- plotData <- read.csv2("exogenous_CC_robert.csv",check.names=FALSE,stringsAsFactors=FALSE) %>% -->
<!--   pivot_longer(cols = 6:12, names_to = "period", values_to = "value") %>% -->
<!--   mutate_at(c('value',"period"), as.numeric)  -->

<!-- plotDataStat <- plotData %>% -->
<!--   group_by(period) %>% -->
<!--   summarise_at(vars(value), list( -->
<!--     Min = min, -->
<!--     Mean = mean, -->
<!--     Median = median, -->
<!--     Max = max, -->
<!--     Sd = sd, -->
<!--     Q1=~quantile(., probs = 0.25, na.rm=TRUE), -->
<!--     Q3=~quantile(., probs = 0.75, na.rm=TRUE))) -->

<!-- g[["Exogenous_Carbon_Capture"]] <- ggplot(plotDataStat,aes(x=period,y=Mean)) + -->
<!--     geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) + -->
<!--     geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") + -->
<!--     geom_line(linewidth=1,color="black") + -->
<!--     geom_ribbon(aes(ymax = Q3, ymin = Q1), alpha = 0.5, fill = "#545454") + -->
<!--     geom_line(aes(y=Min),linewidth=1,color="#545454",linetype = "dashed", alpha = 0.7) + -->
<!--     geom_line(aes(y=Max),linewidth=1,color="#545454",linetype = "dashed", alpha = 0.7) + -->
<!--     #geom_line(data=h,linewidth=1,aes(linetype=Source)) + -->
<!--     #geom_point() + -->
<!--     theme_white() + -->
<!--     #scale_y_continuous(labels = scales::percent_format(accuracy = 1), breaks = seq(0, 1, by = 0.2), limits = c(0,1)) + -->
<!--     theme(axis.title.y=element_blank()) -->

<!-- if(saveCharts){ -->
<!--   ggsave(paste0(chartsFolder,"/svg/Exogenous_Carbon_Capture.svg"), g[["Exogenous_Carbon_Capture"]] , device="svg", width = 12, height = 8, dpi=100, units = "in") -->
<!--   ggsave(paste0(chartsFolder,"/png/Exogenous_Carbon_Capture.png"), g[["Exogenous_Carbon_Capture"]] , device="png", width = 12, height = 8, dpi=100, units = "in") -->
<!-- } -->

<!-- g[["Exogenous_Carbon_Capture_no_outlier"]] <- ggplot(plotDataStat,aes(x=period,y=Mean)) + -->
<!--     geom_hline(yintercept=0, color = "black", linewidth=2, alpha = 0.5) + -->
<!--     geom_vline(xintercept=2020, color = "black", linewidth=1.5, alpha = 0.5,linetype="dashed") + -->
<!--     geom_line(linewidth=1,color="black") + -->
<!--     geom_ribbon(aes(ymax = Q3, ymin = Q1), alpha = 0.5, fill = "#545454") + -->
<!--     theme_white() + -->
<!--     theme(axis.title.y=element_blank()) -->

<!-- if(saveCharts){ -->
<!--   ggsave(paste0(chartsFolder,"/svg/Exogenous_Carbon_Capture_no_outlier.svg"), g[["Exogenous_Carbon_Capture_no_outlier"]] , device="svg", width = 12, height = 8, dpi=100, units = "in") -->
<!--   ggsave(paste0(chartsFolder,"/png/Exogenous_Carbon_Capture_no_outlier.png"), g[["Exogenous_Carbon_Capture_no_outlier"]] , device="png", width = 12, height = 8, dpi=100, units = "in") -->
<!-- } -->

<!-- ``` -->


<!-- ```{r, echo=FALSE, fig.width=12, fig.height=8} -->


<!-- plotDataStat %>% -->
<!--   kbl() %>% -->
<!--   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))  -->

<!--   g[["Exogenous Carbon Capture"]] -->

<!-- ``` -->

# Final Energy 

```{r, echo=FALSE, include=FALSE}

vars <- c(
  "Hydrogen"="Final Energy|Hydrogen",
  "Gases"   ="Final Energy|Gases",
  "Liquids" ="Final Energy|Liquids",
  "Solids"  ="Final Energy|Solids",
  "Other"   ="Final Energy|Other",
  "Heat"    ="Final Energy|Heat",
  "Electricity"="Final Energy|Electricity"
)

plotData <- df %>% filter(variable %in% vars) %>%
  filter(period %in% c(2020,2030,2040,2050),
         scenario == "WP1 NetZero" #,
         #!(model %in% c("LIMES","MEESA","OSeMBE"))
         )

plotData$variable <- factor(plotData$variable , levels = vars)
plotData$model <- factor(plotData$model , levels = c("LIMES","MEESA","OSeMBE", as.character(unique(plotData$model)[!unique(plotData$model) %in% c("LIMES","MEESA","OSeMBE")])))

g[["final_energy_stacked"]] <- ggplot(plotData,aes(x=model,y=value,fill=variable)) +
  geom_hline(yintercept=0, color = "black", linewidth=1, alpha = 0.5) +
  geom_bar(stat='identity') +
  theme_white() +
  facet_wrap(~period, nrow = 1) + 
  scale_fill_manual(values = setNames(color[names(vars)],vars),
                    labels = setNames(names(vars),vars)) +
  ylab("Final Energy (EJ/yr)")

if(saveCharts){
  ggsave(paste0(chartsFolder,"/svg/final_energy_stacked.svg"), g[["final_energy_stacked"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
  ggsave(paste0(chartsFolder,"/png/final_energy_stacked.png"), g[["final_energy_stacked"]] , device="png", width = 12, height = 8, dpi=100, units = "in")
}

g[["final_energy_stacked_2050"]] <- ggplot(plotData %>% filter(period == 2050),aes(x=model,y=value,fill=variable)) +
  geom_hline(yintercept=0, color = "black", linewidth=1, alpha = 0.5) +
  geom_bar(stat='identity') +
  theme_white() +
  facet_wrap(~period, nrow = 1) + 
  scale_fill_manual(values = setNames(color[names(vars)],vars),
                    labels = setNames(names(vars),vars)) +
  ylab("Final Energy (EJ/yr)") +
  theme(legend.position="right")

if(saveCharts){
  ggsave(paste0(chartsFolder,"/svg/final_energy_stacked_2050.svg"), g[["final_energy_stacked_2050"]] , device="svg", width = 12, height = 8, dpi=100, units = "in")
  ggsave(paste0(chartsFolder,"/png/final_energy_stacked_2050.png"), g[["final_energy_stacked_2050"]] , device="png", width = 12, height = 8, dpi=100, units = "in")
}

```


```{r, echo=FALSE, fig.width=12, fig.height=8}

#plotData %>%
#  kbl() %>%
#  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) 

  g[["final_energy_stacked_2050"]]

```


